---
title: 'Exp. 2: Target Detection task with Structured and Random Streams'
author: "Ava Kiai"
date: "23 September, 2020"
output:
  html_document:
  df_print: paged
  pdf_document: default
---

Hi! This script generates all models, tables, analyses, and figures pertaining to Experiment 2 in Kiai & Melloni 2020. Models and data tables at choice points have been saved and can be reloaded using this script, without having to re-run the model or re-wrangle the data. 

```{r}
rm(list=ls()) # clear workspace
# load(".RData") # load saved workspace image for this file

# Working directory is where this file is
setwd(dirname(rstudioapi::getSourceEditorContext()$path))
```

# Paths
```{r}
# Data Path
data_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/1_data/exp_4'
# Code Path
code_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/2_code/exp_4'
# Results Path
res_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/3_results/exp_4'
# Final fig path
fig_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/3_results/final'
```

# Packages and Global Params
```{r message=FALSE}
# latex font for figures
library(extrafont)
loadfonts(device = "win")
par(family="LM Roman 10")

# plot and basic manips
library(tidyverse)

# stats
library(lme4)
library(emmeans)
library(car)
library(broom)
library(fBasics)
library(fitdistrplus)
library(lattice)
library(data.table)

# save tables
library(stargazer)

# Some stuffs for summary stats
source('C:/Users/Ava/Desktop/Experiments/statistical_learning/2_code/summarySE.R')
source('C:/Users/Ava/Desktop/Experiments/statistical_learning/2_code/R_rainclouds.R')

# Global Params
w = 7
h = 5
theme_set(theme_classic(base_size = 22))
```
#----------------------- Preprocessing 
## Load Files (if running through preprocessing)
If you want to skip preprocessing, go to Load Saved Data section and proceed from there!
```{r eval=FALSE, message=FALSE, include=FALSE}
# Load
raw_data <- read_csv(file.path(data_path,'ia_incidental_data_v1.csv'))

# Global Vars
n_subjs_raw <- length(unique(raw_data$subject))
subj_IDs <- unique(raw_data$subject)

# Settings

subjs_SR <- c("t0056","r6364","s3165","u0807","x0805","x5767","h5760","q7907","h4610","k5002")
n_subjs_SR <- length(subjs_SR)
subjs_RS <- c("r9747","g9126","h9453","r5762","n4711","d5450","q5570","l6268","l1982","y7212")
n_subjs_RS <- length(subjs_RS)
    
# Add RT and Hit column to raw data, to be filled in next... 
wrangle_data <- raw_data %>%
    add_column(rt = rep(0,nrow(raw_data)),
               resp = rep(0,nrow(raw_data)))
```
## Calculate RT to each target
Since we loaded the raw data, we need to calculate RTs to target syllables from Presentation-generated log files.
```{r eval=FALSE, include=FALSE}
# for each participant
for (curr_subj_num in 1:n_subjs_raw) {
  curr_subj <- subj_IDs[curr_subj_num]
  curr_subj_data <- wrangle_data[which(wrangle_data$subject==curr_subj),]
    
  # for each trial 
  for (curr_trial in unique(curr_subj_data$trial)) {
  curr_trial_data <- curr_subj_data[which(curr_subj_data$trial==curr_trial),]
    
    # for each condition (rand, struct)
    for (curr_cond in unique(curr_trial_data$sess)) {
    curr_trial_cond_data <- curr_trial_data[which(curr_trial_data$sess==curr_cond),]
    curr_target = curr_trial_cond_data$target[1]
    n_targets <- sum(curr_trial_cond_data$code==curr_target)
    target_times <- curr_trial_cond_data$time[str_which(curr_trial_cond_data$code,curr_target)]
    
# later: confirm that target num max == n_targets | cross-validate with matlab count... 

      for (curr_target_num in 1:length(target_times)) {
        at_next_target = FALSE
        counter = 1
        curr_row = curr_trial_cond_data[which(curr_trial_cond_data$target_num==curr_target_num),]
        row_num = which(curr_trial_cond_data$target_num==curr_target_num)
       
         while (at_next_target == FALSE) {
          curr_row = curr_trial_cond_data[row_num+counter,] # go to next row
          if (is.na(curr_row$subject)) {break} # reached end of trial ...
# later: confirm that two targets don't appear in that window, or else reduce window       
          else if (curr_row$code==1 & curr_row$time<target_times[curr_target_num]+2000) { # resp in 2 sec window...
            curr_trial_cond_data$resp[row_num] = 1 # count a hit
            curr_trial_cond_data$rt[row_num] = curr_row$time-target_times[curr_target_num]} # record RT
          else if (curr_row$code==curr_target) {at_next_target = TRUE} # if it's a target, break/go to next target
          
          counter = counter + 1
        } # go through targets
      } # target
    # add current condition data to table
    curr_trial_data[which(curr_trial_data$sess==curr_cond),] <- curr_trial_cond_data 
    } # condition
    # add current trial data to table
    curr_subj_data[which(curr_subj_data$trial==curr_trial),] <- curr_trial_data
  } # trial
    # add current subject data to complete data table
    wrangle_data[which(wrangle_data$subject==curr_subj),] <- curr_subj_data
} # subject
#view(wrangle_data)
```
## Clean
```{r eval=FALSE, include=FALSE}
# remove all response rows from data set
pre_or_data <- wrangle_data[which(wrangle_data$code!=1),]

# make rt rows where there was no response -> NA
pre_or_data$rt[which(pre_or_data$resp==0)] <- NA

# label condition orders 
pre_or_data <- pre_or_data %>%
    mutate(cond_order = 0,
           cond_ord_n = 0) 
pre_or_data$cond_order[which(pre_or_data$subject %in% subjs_SR)] = "struct-rand"
pre_or_data$cond_order[which(pre_or_data$subject %in% subjs_RS)] = "rand-struct"
pre_or_data$cond_ord_n[which(pre_or_data$subject %in% subjs_SR)] = 1
pre_or_data$cond_ord_n[which(pre_or_data$subject %in% subjs_RS)] = 2 

# make target word for .... 

# factorize where necessary
  pre_or_data <- pre_or_data %>%
    mutate(subject=as_factor(subject),
           trial=as_factor(trial), # essentially, blocks
           code=as_factor(code), # target syllable
           target=as_factor(target), # target syllable
           sess=as_factor(sess), #struct, rand condition
           tgt_pos = as_factor(tgt_pos), 
           tgt_word = as_factor(tgt_word),
           cond_order = as.factor(cond_order))
  
  
# reorder syllable factors along position lines, so they always show up like pos 1's, pos 2's, pos 3's... 
pre_or_data <- pre_or_data %>% mutate(target=fct_reorder(target, as.numeric(tgt_pos)))
    
  
```
## Remove outlier RTs
```{r eval=FALSE, warning=FALSE, include=FALSE}
# view
hist(pre_or_data$rt)
summary(pre_or_data$rt)
ggqqplot(pre_or_data$rt,na.action=na.omit)
sd(pre_or_data$rt,na.rm=TRUE)

#-------------------------------------
# Outlier Removal Method 1: mean +- 3(sd)
# upper_bound <- mean(pre_or_data$rt,na.rm=TRUE)+(3*sd(pre_or_data$rt,na.rm=TRUE))
# lower_bound <- mean(pre_or_data$rt,na.rm=TRUE)-(3*sd(pre_or_data$rt,na.rm=TRUE))
# 
# # filter/ outlier removal based on central tendency 
# or_data1 <- pre_or_data %>%
#   filter(rt > lower_bound | is.na(rt), # keeps NAs, because these are miss markers
#          rt < upper_bound | is.na(rt))
# 
# hist(or_data1$rt)
# ggqqplot(or_data1$rt,na.action=na.omit)
# summary(or_data1$rt)
# sd(or_data1$rt,na.rm=TRUE)
# 
# (data_loss_mean <- 1-length(or_data1$rt)/length(pre_or_data$rt))

#-------------------------------------
# Outlier Removal Method 2: median +- 3(mad) 
# --> https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/mad
    # MAD = b Mi(|xi−Mj(xj)|), where x = n orig. observations; and M is the median of the series
    # Usually, b = 1.4826, a constant linked to the assumption of
    # normality of the data, disregarding the abnormality induced by outliers
    # (Rousseeuw & Croux, 1993).
    # If another underlying distribution is assumed (which is seldom
    # the case in the field of psychology), this value changes to b = 1/
    # Q(0.75), where Q(0.75) is the 0.75 quantile of that underlying distribution.
    # In case of normality, 1/Q(0.75) = 1.4826 (Huber, 1981). This
    # multiplication by b is crucial, as otherwise the formula for the MAD
    # would only estimate the scale up to a multiplicative constant.
    # Concretely, calculating the MAD implies the following steps:
    # (a) the series in which the median is subtracted of each observation
    # becomes the series of absolute values of (1–7), (3–7), (3–7), (6–7),
    # (8–7), (10–7), (10–7), and (1000–7), that is, 6, 4, 4, 1, 1, 3, 3, and
    # 993; (b) when ranked, we obtain: 1, 1, 3, 3, 4, 4, 6, and 993; (c) and
    # (d) the median equals 3.5 and will be multiplied by 1.4826 to find a
    # MAD of 5.1891.
mad_norm <- mad(pre_or_data$rt,na.rm=TRUE)

upper_bound_med <- median(pre_or_data$rt,na.rm=TRUE)+(3*mad_norm)
lower_bound_med <- median(pre_or_data$rt,na.rm=TRUE)-(3*mad_norm)

# filter 
or_data2 <- pre_or_data %>%
  dplyr::filter(rt > lower_bound_med | is.na(rt), # keeps NAs, because these are miss markers
         rt < upper_bound_med | is.na(rt))

hist(or_data2$rt)
#qqplot(or_data2$rt,na.action=na.omit)
summary(or_data2$rt)
sd(or_data2$rt,na.rm=TRUE)

(data_loss_med <- 1-length(or_data2$rt)/length(pre_or_data$rt))

#-------------------------------------
# Outlier Removal Method 3: median +- 3(mad mult. by 1/Q(0.75)) 
# mad_75_qnt <- unname(mad(pre_or_data$rt,constant=1/(quantile(pre_or_data$rt,na.rm=TRUE)[4]),na.rm=TRUE)) # does that fact that these are different suggest that, outliers aside, the underlying distribution is still not normal?
# 
# upper_bound_med_75 <- median(pre_or_data$rt,na.rm=TRUE)+(3*mad_75_qnt)
# lower_bound_med_75 <- median(pre_or_data$rt,na.rm=TRUE)-(3*mad_75_qnt)
# 
# # filter 
# or_data3 <- pre_or_data %>%
#   filter(rt > lower_bound_med_75 | is.na(rt), # keeps NAs, because these are miss markers
#          rt < upper_bound_med_75 | is.na(rt))
# 
# hist(or_data3$rt)
# ggqqplot(or_data3$rt,na.action=na.omit)
# summary(or_data3$rt)
# sd(or_data3$rt,na.rm=TRUE)
# 
# (data_loss_med <- 1-length(or_data3$rt)/length(pre_or_data$rt))

# output... Chose the method of median +- 3 mad() based on the assumption of normality and a b of 1.48...
data <- or_data2

```
We chose method 2 (median +- 3(median absolute deviation)) as the outlier removal method. This method maintained a fair amount of the data (data loss of 5.79%). The median was roughly unchanged (525.5 to 529.4 ms), while the min/max became more symmetric around the median. 
While the mean +- 3(sd) method had also preserved much of the data (data loss of 1.93%), it left many extreme values in place, leading to a much more skewed qqplot. -- QQplots tell us about the normality of the underlying distribution. Although RT distributions are skewed, and in fact take the form of an exponential gaussian (gaussian convolved with an exponential function, and captured by parameters mu, sigma, and tau), we hope to remove extreme values at the tails that may not be informative. We do this based on a measure of central tendency not affected by the value of extreme outliers. For ref, see: Leys et al. 2013.
## Count Hits
```{r eval=FALSE, include=FALSE}
n_total_targets <- length(pre_or_data$rt) 

n_missed <- length(which(is.na(pre_or_data$rt))) # the same before and after OR

# Before Outlier Removal  
n_hits_W.O <- length(which(!is.na(pre_or_data$rt)))
(hit_rate <- n_hits_W.O/n_total_targets)
(miss_rate <- n_missed/n_total_targets)

# After Outlier Removal 
n_targets_OR <- length(data$rt)
n_hits_O.R <- length(which(!is.na(data$rt))) 
(hit_rate_O.R <- n_hits_O.R/n_targets_OR)
(miss_rate <- n_missed/n_targets_OR)



```
Outlier removal brought hit rate down from 83.06% to 82.02% - a marginal change.
There were 1430 NAs or missed targets (miss rate was 16.93%, now 17.97%).
#----------------------- ANALYSES
# Load Saved TD
```{r}
data <- read_csv("C:/Users/Ava/Desktop/Experiments/statistical_learning/1_data/exp_4/exp_4_rt_data.csv") %>%
  mutate(subject = as.factor(subject),
         target = as.factor(target),
         sess = as.factor(sess), 
         tgt_pos = as.factor(tgt_pos), 
         tgt_word = as.factor(tgt_word),
         cond_order = as.factor(cond_order))
```

#1. Accuracy
## Summarize
```{r}
data %>% summarySE(measurevar = "resp",na.rm=TRUE) 

base_acc1 <- data %>% summarySE(measurevar = "resp", groupvars = c("subject"),na.rm=TRUE)

t.test(base_acc1$resp_mean, mu = 0.5, alternative = "greater")

data %>% summarySE(measurevar = "resp", groupvars = c("sess"),na.rm=TRUE) 

base_acc2 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","subject"),na.rm=TRUE) 

t.test(base_acc2$resp_mean[which(base_acc2$sess=="rand")],
       base_acc2$resp_mean[which(base_acc2$sess=="struct")],
       alternative = "less") # h1 = y is larger than x
```

## a. Plot Session x Position 
```{r}
accuracy_data1 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","tgt_pos","subject"),na.rm=TRUE) 
accuracy_data2 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","tgt_pos"),na.rm=TRUE)

# ---- On averaged across participants
pos.lm <- lm(resp_mean ~ tgt_pos, data=dplyr::filter(accuracy_data1,sess=="struct"))
summary(pos.lm)
Anova(pos.lm, type = '2')
(emmeans(pos.lm, specs = pairwise ~ tgt_pos))
 
```


```{r}
ggplot(accuracy_data1, aes(x = tgt_pos, y = resp_mean, fill = tgt_pos)) +
   geom_point(position = position_jitter(width = .07)) +
   geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 0.8, trim = FALSE) + 
   geom_point(accuracy_data2, mapping = aes(tgt_pos, resp_mean), position = position_nudge(x = 0.2, y = 0)) +
   geom_errorbar(accuracy_data2, mapping=aes(tgt_pos, y=resp_mean, ymin=resp_mean-se,
                                             ymax=resp_mean+se),
                 position = position_nudge(x = 0.2, y = 0), width = 0.05, size = 1) +
 # geom_col(accuracy_data2, mapping=aes(sess, resp_mean, group=as.factor(tgt_pos), fill=as.factor(tgt_pos)), 
 #          position = position_dodge(0.5), width=0.5) +
 # geom_errorbar(accuracy_data2, mapping=aes(sess, y=resp_mean, ymin=resp_mean-se, ymax=resp_mean+se,
 #          group=tgt_pos,color=as.factor(tgt_pos)), position=position_dodge(0.5), width = 0.3, size = 1) +
 # geom_signif(comparisons=list(c("rand", "struct")), annotations="***", y_position=0.95, tip_length=0.3) + 
  facet_grid(.~ sess) +
  scale_x_discrete(name = "Target Position") +
  scale_y_continuous(name = "mean detection accuracy [bars = SEM]") +
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Pastel2") +
  scale_y_continuous(limits = c(0,1), name = "mean detection accuracy [bars = SEM]") +
  scale_x_discrete(name = "Target Position") +
  guides(fill = FALSE, color = FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold"))#+
  #ggsave(file.path(fig_path,'exp4_acc_fig1.png'),width=w,height=h)
```

Stats
```{r eval=FALSE, include=FALSE}
# ANOVA
# use lm() then car::Anova() to evaluate model (because allows Types I, II & III Sums of squares*)
acc.mod1 <- lm(resp_mean ~ sess * tgt_pos, data=accuracy_data1)
Anova(acc.mod1, type = '2')
  # to investigate your options... 
  class(acc.mod1)
  methods(class="lm") # asses available methods to run on lm() output

acc.mod2 <- lm(resp_mean ~ sess + tgt_pos, data=accuracy_data1)
Anova(acc.mod2, type = '2')

# use stats::anova() to compare models 
anova(acc.mod1, acc.mod2, test = 'Chisq')
# -> they are the same, because it seems there's no interaction...

# extract least square mean contrasts
(em.sess <- emmeans(acc.mod2, specs = pairwise ~ sess)) 

(em.tgtpos.sess <- emmeans(acc.mod2, specs = pairwise ~ sess|tgt_pos)) 

(em.sess.tgtpos <- emmeans(acc.mod2, specs = pairwise ~ tgt_pos|sess)) 

acc.table <- as.data.frame(Anova(acc.mod1, type = '2'))

em.acc <- em.sess.tgtpos$contrasts %>%
    summary(infer=TRUE) %>%
     rbind() %>%
     as.data.frame()
plot(em.sess, comparisons = TRUE)
plot(em.sess.tgtpos, comparisons = TRUE)


```
Significant effect of session. 
No effect of target position. 

## b. Plot Target Word
```{r}
accuracy_data3 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","tgt_word","subject"),na.rm=TRUE) %>%
  mutate(tgt_word = case_when(tgt_word==1 ~ "nugadi",
                         tgt_word==2 ~ "rokise",
                         tgt_word==3 ~ "mipola",
                         tgt_word==4 ~ "zabetu"))
accuracy_data4 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","tgt_word"),na.rm=TRUE)
accuracy_data4$tgt_word <- rep(c("nugadi","rokise","mipola","zabetu"),2)
stargazer(accuracy_data4, 
          type = "html", 
          out = file.path(res_path,'tables','word_accuracy.doc'), summary = FALSE, rownames = FALSE)

# ---- On averaged across participants
word.lm <- lm(resp_mean ~ tgt_word, data=dplyr::filter(accuracy_data3,sess=="struct"))
summary(word.lm)
Anova(word.lm, type = '2')
(emmeans(word.lm, specs = pairwise ~ tgt_word))

```


```{r}
ggplot(accuracy_data3, aes(x = tgt_word, y = resp_mean, fill = tgt_word)) +
   geom_point(position = position_jitter(width = .07)) +
   geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 0.8, trim = FALSE) + 
   geom_point(accuracy_data4, mapping = aes(tgt_word, resp_mean), position = position_nudge(x = 0.2, y = 0)) +
   geom_errorbar(accuracy_data4, mapping=aes(tgt_word, y=resp_mean, ymin=resp_mean-se,
                                             ymax=resp_mean+se),
                 position = position_nudge(x = 0.2, y = 0), width = 0.05, size = 1) +
  facet_grid(.~ sess) +
  scale_fill_manual(values=wes_palette("Zissou1")[c(1,3,4,5)]) +
  scale_y_continuous(limits = c(0,1), name = "mean detection accuracy [bars = SEM]") +
  scale_x_discrete(name = "Pseudoword", labels = c("nugadi","rokise","mipola","zabetu")) + 
  guides(fill = FALSE, color = FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) #+
#  ggsave(file.path(fig_path,'exp4_acc_fig2.png'),width=w,height=h)
```


## c. Plot Target Syllable
```{r}
accuracy_data5 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","target","subject", "tgt_pos"),na.rm=TRUE) %>%
  mutate(target = factor(target, levels = c("nu","ga","di","ro","ki","se","mi","po","la","za","be","tu")))
accuracy_data6 <- data %>% summarySE(measurevar = "resp", groupvars = c("sess","target","tgt_pos"),na.rm=TRUE) %>%
  mutate(target = factor(target, levels = c("nu","ga","di","ro","ki","se","mi","po","la","za","be","tu")))

stargazer(accuracy_data6, 
          type = "html", 
          out = file.path(res_path,'tables','syllable_accuracy.doc'), summary = FALSE, rownames = FALSE)

# ---- On the averaged data
target.lm <- lm(resp_mean ~ target*sess, data=accuracy_data5)
summary(target.lm)
Anova(target.lm)
# Contrasts & Cohen's d
(emmeans(target.lm, specs = pairwise ~ sess, adjust = "tukey", transform = "response"))
(as.data.frame(emmeans(target.lm, specs = pairwise ~ sess, adjust = "tukey", transform = "response")$contrasts)$estimate / sigmaHat(target.lm))


(target.emm <- emmeans(target.lm, specs = pairwise ~ target, adjust = "tukey", transform = "response"))
(as.data.frame(target.emm$contrasts)$estimate / sigmaHat(target.lm))

as.data.frame(target.emm$contrasts)[which(as.data.frame(target.emm$contrasts)$p.value < 0.05),]


emmip(target.lm, sess~target, CIs = TRUE)

# There's a main effect of target and session. That means some targets (syllables) were more easy or more difficult to detect. However, we need to account in the model for the fact that identity is confounded with position -- if the variation is entirely due to structure, then we need not worry about identity. 
# In struct-rand contrasts, only tu and mi were different. 
# 
# No pairs were sig. different within levels of session. 
# 
# An effect of session suggests that whether those syllables were embedded in words or not had an effect on detectability.
# 
# There's no interaction, which suggests that embedding did not modulate the differences between syllables in the detectability. 
```

## Fig. S1b. Accuracy ~ Syllable
```{r}
ggplot() + 
  #(accuracy_data5, aes(x = target, y = resp_mean)) +
  #geom_point(position = position_jitter(width = .07), aes(color = tgt_pos)) +
  #geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 1, trim = FALSE,
  #                 fill = "gray") + 
  geom_errorbar(accuracy_data6, mapping=aes(target, y=resp_mean, ymin=resp_mean-se,ymax=resp_mean+se),     
                position = position_nudge(x = 0.0, y = 0), width = 0.5, size = 1) +
  geom_line(accuracy_data6, mapping = aes(target,resp_mean,group = sess, linetype = sess),size = 1) +
  geom_point(accuracy_data6, mapping = aes(target, resp_mean, color = tgt_pos), size = 4, position = position_nudge(x = 0.0, y = 0)) +
  #facet_grid(.~sess) + 
  scale_color_brewer(palette="Dark2") + 
 # scale_color_manual(values = c("#1B9E77","#D95F02","#7570B3","#E41A1C","#377EB8")) +
#  scale_color_manual(values = c("#ABABAB", "#757575", "#454545","#E41A1C","#377EB8")) + # From RColorBrewer::brewer.pal(3,"Set1")[1:2]
  scale_y_continuous(limits = c(0,1), name = "Mean detection accuracy") +
  scale_x_discrete(name = "Target syllables") + 
  scale_linetype_manual(name = "Condition", values = c('solid', 'dashed')) + 
  guides(color = FALSE) + labs(color = "Ordinal position") +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size = 22), legend.position = "top") +
  ggsave(file.path(fig_path,'exp4_accuracy_syll.png'),width=7,height=6)
```

### Regress out syllable effect
```{r}
# across all participants, median RTs for each of the syllables
# rm anova with syllable and position as factors
subj.mod <- glmer(rt_secs ~ tgt_pos*target + (1 | subject), data = data, family = Gamma("log"), control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(subj.mod)
### rt_secs!

# for each participant, subtracted the residual RT value from observed value for each syllable, co-varying out the effects of physical stimulus factors and yielding corrected RT effect

# Model is rank-deficient

broom.mixed::glance(subj.mod)
broom.mixed::augment(subj.mod)
data_adj <- data.frame(subject = as.factor(augment(subj.mod)$subject),
           tgt_pos = as.factor(augment(subj.mod)$tgt_pos),
           rt_adj = as.numeric(augment(subj.mod)$rt_secs - augment(subj.mod)$.resid))
         
rt.mod.less.int.adj <- glmer(rt_adj ~ 1 + tgt_pos + (1 | subject), data = data_adj, family = Gamma(link = "log"))
  summary(rt.mod.less.int.adj)
  plot(residuals(rt.mod.less.int.adj))
  qqnorm(resid(rt.mod.less.int.adj))
  
  Anova(rt.mod.less.int.adj)
  
  
reg.syll.mod <- (emmeans(rt.mod.less.int.adj, specs = pairwise ~ tgt_pos, adjust = "Tukey", transform = "response"))  
reg.mod.cont <- as.data.frame(reg.syll.mod$contrasts)
(reg.mod.cont$d <- reg.mod.cont$estimate / sigmaHat(rt.mod.less.int.adj))
```

### Prove OR removal didn't change it
Uncomment and run this only if preprocessing chunks were executed and pre_or_data is in workspace. 
```{r}

# pre_or_data %>%
#   summarise(mean = mean(resp),
#             sd = sd(resp))
# 
# after <- data %>% summarySE(measurevar = "resp", groupvars = c("subject"),na.rm=TRUE)
# before <- pre_or_data %>% summarySE(measurevar = "resp", groupvars = c("subject"),na.rm=TRUE)
# 
# t.test(after$resp_mean, before$resp_mean, alternative = "two.sided")

```


### RT ~ Position - Individuals
```{r message=FALSE}
data_sum7 <- data %>%
    summarySE(measurevar="rt", groupvars=c("subject","tgt_pos","sess","trial","tgt_word"), na.rm=TRUE)
data_sum8 <- data %>%
    summarySE(measurevar="rt", groupvars=c("subject","tgt_pos","sess"), na.rm=TRUE)

subj.labs <- (unique(data$subject)) # what labels should say
names(subj.labs) <- (c(1:20)) # names are as they appear in the df

# Median +- CI
ggplot() +
  geom_point(data = data_sum7, mapping = aes(x=tgt_pos,y=rt_median, colour = factor(tgt_word)), size = 2) +
  geom_line(data = data_sum7, mapping = aes(x = tgt_pos, y = rt_median, group = tgt_word), colour = "GREY",size = .5) +
  geom_point(data = data_sum8, mapping = aes(x = tgt_pos, y = rt_median), colour = "BLACK") +
  geom_errorbar(data = data_sum8, mapping = aes(x = tgt_pos, y = rt_median, ymin = rt_median-ci, ymax = rt_median+ci), colour = "BLACK", width = 0.1, size = 0.8) +
  geom_line(data = data_sum8, mapping = aes(x = tgt_pos, y = rt_median, group = 1), colour = "BLACK", size = .9) +
  facet_grid(sess ~ subject, labeller = labeller(subject = subj.labs),switch = "y") +
  scale_colour_brewer(palette = "Paired") +
  labs(colour= "Trials (Word)") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Target Postion') +
  scale_x_discrete(limits=c(1:3)) +
  theme_bw() +
  theme(text = element_text(family = "LM Roman 10", face="bold"))# +
 # ggsave('targetdetection_facet.png', width = 20, height = 4)
```


# 2. RT Data by Position - Test
## Summarize
```{r}
# Show RT for each position & each trial (in this case the same thing as tgt_word)
data_sum1 <- data %>%
    summarySE(measurevar="rt", groupvars=c("tgt_pos","tgt_word","sess"), na.rm=TRUE)
    data_sum1_struct <- data_sum1 %>% filter(sess == "struct")
    data_sum1_rand <- data_sum1 %>% filter(sess == "rand")
    
# Show RT for each position only
data_sum2 <- data %>%
    summarySE(measurevar="rt", groupvars=c("tgt_pos","sess"), na.rm=TRUE)
    data_sum2_struct <- data_sum2 %>% filter(sess == "struct")
    data_sum2_rand <- data_sum2 %>% filter(sess == "rand")

# filter
data_SR <- data %>%
  filter(data$cond_ord_n==1)
data_RS <- data %>%
  filter(data$cond_ord_n==2)

# Show RT for each position & each trial (in this case the same thing as tgt_word)
data_SR_sum1 <- data_SR %>%
    summarySE(measurevar = "rt", groupvars = c("tgt_pos","tgt_word","sess"),na.rm=TRUE)
# Show RT for each position only
data_SR_sum2 <- data_SR %>%
    summarySE(measurevar = "rt", groupvars = c("tgt_pos","sess"),na.rm=TRUE)

# Show RT for each position & each trial (in this case the same thing as tgt_word)
data_RS_sum1 <- data_RS %>%
    summarySE(measurevar = "rt", groupvars = c("tgt_pos","tgt_word","sess"),na.rm=TRUE)
# Show RT for each position only
data_RS_sum2 <- data_RS %>%
    summarySE(measurevar = "rt", groupvars = c("tgt_pos","sess"),na.rm=TRUE)


```

## Fig. 1a. RT ~ Pos | Sess
```{r}
# Median +- CI
ggplot() +
  #geom_point(data = data_sum1, mapping = aes(x=tgt_pos,y=rt_median, colour = factor(tgt_word)), size = 2) +
  #geom_line(data = data_sum1, mapping = aes(x = tgt_pos, y = rt_median, group = tgt_word, colour = factor(tgt_word)),size = .5) +
  geom_point(data = data_sum2, mapping = aes(x = tgt_pos, y = rt_median),
                #                             color = sess)) +
                color = "black", size = 2)+
  geom_errorbar(data = data_sum2, mapping = aes(x = tgt_pos, y = rt_median, ymin = rt_median-ci, ymax = rt_median+ci),
                 #                               color=sess), 
                color = "black",
                width = 0.1, size = 0.8) +
  geom_line(data = data_sum2, mapping = aes(x = tgt_pos, y = rt_median, group = sess,
                                            linetype = sess), 
            color = "black",
            size = .9) +
  #facet_grid(.~ sess) +
 # scale_colour_brewer(name = "condition",palette = "Set1") +
  #labs(colour= "Trial (Word)") + 
  ylab('Median RT (ms)') + 
  xlab('Ordinal postion') +
  scale_x_discrete(limits=c(1:3)) +
  scale_linetype_manual(name = "condition", values = c('solid', 'dashed')) + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size=22),legend.position=c(0.8,0.9)) +
  ggsave(file.path(fig_path,'targetdetection_overall_median_overlap.png'), width = w, height = h)

```


```{r}
data_SR_sum1$sess <- factor(data_SR_sum1$sess, levels=c("struct","rand"))
data_SR_sum2$sess <- factor(data_SR_sum2$sess, levels=c("struct","rand"))
```

## Fig. S5a. Struct>Rand
```{r}
# Median +- CI
ggplot() +
 # geom_point(data = data_SR_sum1, mapping = aes(x=tgt_pos,y=rt_median, colour = factor(tgt_word)), size = 2) +
#  geom_line(data = data_SR_sum1, mapping = aes(x = tgt_pos, y = rt_median, group = tgt_word, colour = factor(tgt_word)),size = .5) +
  geom_point(data = data_SR_sum2, mapping = aes(x = tgt_pos, y = rt_median), size = 2) +
  geom_errorbar(data = data_SR_sum2, mapping = aes(x = tgt_pos, y = rt_median, ymin = rt_median-ci, ymax = rt_median+ci), width = 0.1, size = 0.8) +
  geom_line(data = data_SR_sum2, mapping = aes(x = tgt_pos, y = rt_median, group = sess, linetype = sess), 
            color = "black",
            size = .9) +
 # facet_grid(.~ sess) +
 # scale_colour_brewer(name = "condition",palette = "Set1") +
#  scale_colour_brewer(palette = "Paired") +
 # labs(colour= "Trial (Word)") + 
  ylab('Median RT (ms)') + xlab('Ordinal postion') +
  scale_x_discrete(limits=c(1:3)) +
  scale_linetype_manual(name = "condition", values = c('dashed', 'solid')) + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size = 22),legend.position=c(0.8,0.9)) +
  ggsave(file.path(fig_path,'s5_condition_order_StructRand.png'), width = w, height = h)

```
## Fig. S5b. Rand>Struct
```{r}
# Median +- CI
ggplot() +
 # geom_point(data = data_RS_sum1, mapping = aes(x=tgt_pos,y=rt_median, colour = factor(tgt_word)), size = 2) +
#  geom_line(data = data_RS_sum1, mapping = aes(x = tgt_pos, y = rt_median, group = tgt_word, colour = factor(tgt_word)),size = .5) +
  geom_point(data = data_RS_sum2, mapping = aes(x = tgt_pos, y = rt_median), size = 2) +
  geom_errorbar(data = data_RS_sum2, mapping = aes(x = tgt_pos, y = rt_median, ymin = rt_median-ci, ymax = rt_median+ci),  width = 0.1, size = 0.8) +
  geom_line(data = data_RS_sum2, mapping = aes(x = tgt_pos, y = rt_median, group = sess, linetype = sess), 
            color = "black",
            size = .9) +
 # facet_grid(.~ sess) +
#  scale_colour_brewer(name = "condition",palette = "Set1") +
  #scale_colour_brewer(palette = "Paired") +
  #labs(colour= "Trial (Word)") + 
  ylab('Median RT (ms)') + xlab('Ordinal postion') +
  scale_linetype_manual(name = "condition", values = c('solid', 'dashed')) + 
  scale_x_discrete(limits=c(1:3)) +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size=22),legend.position=c(0.8,0.9)) +
  ggsave(file.path(fig_path,'s5_condition_order_RandStruct.png'), width = w, height = h)

```

## Fig. 1b. Rainclouds
```{r}
data_sum1b <- data %>% # target position x subject
    summarySE(measurevar = "rt", groupvars = c("tgt_pos","subject","sess"),na.rm=TRUE)
    
ggplot(data_sum1b, aes(x = tgt_pos, y = rt_median, fill = tgt_pos)) +
  geom_point(position = position_jitter(width = .07)) +
  geom_flat_violin(aes(linetype=sess),position = position_nudge(x = 0.2, y = 0), adjust = 1, trim = TRUE) + 
  geom_boxplot(aes(linetype=sess),width = 0.1, alpha = 0.5, position = position_nudge(x=0.2,y=0)) +
  facet_grid(.~ sess) +
  #scale_fill_manual(values=wes_palette("Royal2")[c(3,4,5)]) +
  scale_fill_brewer(palette="Dark2") + 
#  scale_fill_brewer(palette="Pastel2") +
#  scale_y_continuous(limits=c(380,580)) +
#  labs(fill = "position") +
  ylab('Median RT (ms)') + 
  xlab('Ordinal postion') +
  guides(fill = FALSE) + 
  scale_linetype_manual(name = "cond.", values = c('solid', 'dashed')) + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size=22),legend.position=c(0.93,0.9),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggsave(file.path(fig_path,'exp4fig1b_rt_pos.png'), width = w, height = h)

```

# 3. RT Data by Target - Control
## Summarize
```{r warning=FALSE}
# Show RT for position, syllable, session
data_sum3 <- data %>%
    summarySE(measurevar="rt", groupvars=c("tgt_pos","target","sess","subject"), na.rm=TRUE) 

# Show RT for session & syllable
data_sum4 <- data %>%
    summarySE(measurevar="rt", groupvars=c("target","sess"), na.rm=TRUE) 

# Show RT for position, syllable, session, condition order
data_sum5 <- data %>%
    summarySE(measurevar="rt", groupvars=c("tgt_pos","target","sess","subject","cond_order"), na.rm=TRUE) 
  
# Show RT for session & syllable & condition order
data_sum6 <- data %>%
    summarySE(measurevar="rt", groupvars=c("target","sess","cond_order"), na.rm=TRUE) 


```

## a. Plot Targets
```{r warning=FALSE}
ggplot() +
  geom_point(data = data_sum3, mapping = aes(x=target, y=rt_median, colour = tgt_pos), size = 2) +
  geom_smooth(data = data_sum4, mapping = aes(x =target, y = rt_median, group=1), ci=TRUE,size=1, colour="BLACK") +
  facet_grid(.~ sess) +
  scale_colour_brewer(palette = "Set2") +
  labs(colour= "Target Position") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Syllable (Target)') +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold"))# +
  #ggsave('targetdetection_syllable.png', width = w, height = h+1)
```
  # Note: an effect of session, but not condition order

## b. Overlay Targets in each Condition
```{r warning=FALSE}
ggplot(data=data_sum4, mapping=aes(x=target, y=rt_median, color=sess)) +
  geom_point(size=1.5) +
  geom_smooth(aes(group=sess, fill=sess), ci=TRUE, size=1) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Pastel1") +
  labs(colour= "Condition") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Syllable (Target)') +
  guides(fill=FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) #+
 # ggsave('targetdetection_syllable_overlay.png', width = w, height = h+1)

ggplot(data=data_sum4, mapping=aes(x=target, y=rt_mean, color=sess)) +
  geom_point(size=1.5) +
  geom_smooth(aes(group=sess, fill=sess), se=TRUE, size=1) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Pastel1") +
  labs(colour= "Condition") + ylab('Mean Response Time (ms) [bars = SEM]') + xlab('Syllable (Target)') +
  guides(fill=FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold"))# +
 # ggsave('targetdetection_syllable_overlay_mean.png', width = w, height = h+1)

```

## c. Plot Targets, Orders
```{r}
# Struct -> Rand
data_sum5 %>%
  dplyr::filter(cond_order=="struct-rand") %>%
ggplot() +
  geom_point(mapping=aes(x=target, y=rt_median, colour = tgt_pos), size = 2) +
  geom_smooth(data=dplyr::filter(data_sum6,cond_order=="struct-rand"), mapping = aes(x = target, y = rt_median, group=1), ci=TRUE,size=1, colour="BLACK") +
  facet_grid(.~ fct_rev(sess)) +
  scale_colour_brewer(palette = "Set2") +
  labs(colour= "Target Position") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Syllable (Target)') +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggtitle("Struct - Rand") #+ 
 # ggsave('targetdetection_syllable_SR.png', width = w, height = h+1)

# Rand -> Struct
data_sum5 %>%
  dplyr::filter(cond_order=="rand-struct") %>%
ggplot() +
  geom_point(mapping=aes(x=target, y=rt_median, colour = tgt_pos), size = 2) +
  geom_smooth(data=dplyr::filter(data_sum6,cond_order=="rand-struct"), mapping = aes(x = target, y = rt_median, group=1), ci=TRUE,size=1, colour="BLACK") +
  facet_grid(.~ sess) +
  scale_colour_brewer(palette = "Set2") +
  labs(colour= "Target Position") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Syllable (Target)') +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggtitle("B. Rand - Struct")# +
 # ggsave('targetdetection_syllable_RS.png', width = w, height = h+1)


```

## d. Overlay Targets, Orders
```{r}
# Struct -> Rand
ggplot(data=dplyr::filter(data_sum6,cond_order=="struct-rand"), mapping=aes(x=target, y=rt_median, colour=sess)) +
  geom_point(size=1.5) +
  geom_smooth(aes(group=sess, fill=sess), ci=TRUE, size=1) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Pastel1") +
  labs(colour= "Condition") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Syllable (Target)') +
  guides(fill=FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggtitle("Struct - Rand") #+ 
 # ggsave('targetdetection_syllable_SR_overlay_median.png', width = w, height = h+1)

# Rand -> Struct
ggplot(data=dplyr::filter(data_sum6,cond_order=="rand-struct"),mapping=aes(x=target, y=rt_median, colour=sess)) +
  geom_point(size=1.5) +
  geom_smooth(aes(group=sess, fill=sess), ci=TRUE, size=1) +
  scale_colour_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Pastel1") +
  labs(colour= "Condition") + ylab('Median Response Time (ms) [bars = CI]') + xlab('Syllable (Target)') +
  guides(fill=FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggtitle("Rand - Struct")# +
  #ggsave('targetdetection_syllable_RS_overlay_median.png', width = w, height = h+1)

```

# 4. GLMMs
```{r}
data <- data %>%
  mutate(rt_secs = rt/1000)

data %>% summarySE(., measurevar = "rt_secs", groupvars = c("sess","tgt_pos"), na.rm = TRUE)

```

Save TD Data
```{r}
# write.csv(data,file.path("C:/Users/Ava/Desktop/Experiments/interval_adjust/r_scripts_v1/exp_4_rt_data.csv"), row.names = FALSE)
```

## Load Winning GLM
```{r}
load(file.path(res_path,'models','glm_less_slope_sessrand.Rdata'))
```

## Normality
```{r}
# Normality
shapiro.test(log10(sample(data$rt_secs[!is.na(data$rt_secs)],size=5000,replace=FALSE)))
# --> data is not even log normal...
```

## Dist Fit
Our RT data is continuous, non-zero, and positively skewed. 
```{r}
# Very useful resource!: http://www.di.fc.ul.pt/~jpn/r/distributions/fitting.html
# Explore
hist(data$rt, main = "RT Histogram")
plot(density(data$rt[!is.na(data$rt_secs)]), main = "RT Density Estimates")
plot(ecdf(data$rt[!is.na(data$rt_secs)]), main = "RT Cumulative Distribution")


# Params
mean <- mean(data$rt[!is.na(data$rt_secs)])
sd <- sd(data$rt[!is.na(data$rt_secs)])
rts <- data$rt[!is.na(data$rt_secs)]
rt.z.norm<-(rts-mean)/sd ## standardized data
n_dist <- length(rt.z.norm)

skewness(rt.z.norm)
kurtosis(rt.z.norm)

# Explore Basic Fits using QQ
# Normal? Nope.
qqnorm(rt.z.norm, main = "RT QQ for Norm Dist.") ## drawing the QQplot
abline(0,1) 
# h<-hist(rts,breaks=15)
# xhist<-c(min(h$breaks),h$breaks)
# yhist<-c(0,h$density,0)
# xfit<-seq(min(rts),max(rts),length=40)
# yfit<- dnorm(xfit,mean,sd)
# plot(xhist,yhist,type="s",ylim=c(0,max(yhist,yfit)), main="Normal pdf and histogram")
# lines(xfit,yfit, col="red")

# Early guess: Gamma? Mhm.
theo.gamma <-rgamma(n=n_dist, shape=mean, scale=sd) ## theorical quantiles given our m, sd
hist(theo.gamma, main = "Gamma distribution")
qqplot(rt.z.norm,theo.gamma, main="RT QQ for Gamma Dist.") 

# Goodness of fit using fitdistr and overlaying hist with pdf of theo.


descdist(rts, discrete = FALSE)
descdist(rts, discrete = FALSE, boot = 500)
# lognormal, gamma, and weibull are all candidates
fit.wei  <- fitdist(rts, "weibull")
fit.gam  <- fitdist(rts, "gamma")
fit.ln <- fitdist(rts, "lnorm")
summary(fit.wei)
summary(fit.gam)
summary(fit.ln)

par(mfrow=c(2,2))
plot.legend <- c("Weibull", "lognormal", "gamma")
denscomp(list(fit.wei, fit.gam, fit.ln), legendtext = plot.legend)
cdfcomp (list(fit.wei, fit.gam, fit.ln), legendtext = plot.legend)
qqcomp  (list(fit.wei, fit.gam, fit.ln), legendtext = plot.legend)
ppcomp  (list(fit.wei, fit.gam, fit.ln), legendtext = plot.legend)

gofstat(list(fit.wei, fit.gam, fit.ln), fitnames = c("weibull", "gamma", "lognorm"))
```
Could be described by a lognormal or gamma distribution. 


## a. Session * Target Position
```{r}
options(contrasts = c("contr.sum", "contr.poly"))
glm.less.int <- glmer(rt_secs ~ sess * tgt_pos + (1 | cond_order/subject), data = data, family = Gamma(link = "log"))
  summary(glm.less.int)
  plot(resid(glm.less.int))
  qqnorm(resid(glm.less.int))
  Anova(glm.less.int)
  save(glm.less.int,file = "e4glm_less_int.Rdata")
```

## b. Session * Condition Order * Target Position
```{r}
glm.fuller.int <- glmer(rt_secs ~ sess * cond_order * tgt_pos + (1 | cond_order/subject), data = data, family = Gamma(link = "log"),
                        control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(glm.fuller.int) 
  plot(resid(glm.fuller.int))
  qqnorm(resid(glm.fuller.int))
  Anova(glm.fuller.int)
  save(glm.fuller.int,file = "e4glm_full_int.Rdata")

anova(glm.less.int,glm.fuller.int)

coef(glm.fuller.int)
```


```{r}
(em.test <- emmeans(glm.fuller.int, specs = pairwise ~ cond_order|tgt_pos*sess, adjust = "tukey", transform = "response"))

em.glm.d.sess.tgt.pairs <- em.glm.d.sess.tgt$contrasts %>%
     summary(infer=TRUE) %>%
     rbind() %>%
     as.data.frame()


poslabels <- c(
  `tgt_pos: 1` = "Pos 1",
  `tgt_pos: 2` = "Pos 2",
  `tgt_pos: 3` = "Pos 3")
  `sess: rand` = "rand",
  `sess: struct` = "struct")

png(file = 'exp4figS4.png', width = w, height = h, res = 300, units = "in")
plot(em.test, comparisons = TRUE) +
  xlab("estimated marginal means") +
  ylab("session order") + 
  facet_grid(tgt_pos+sess ~ .) + 
  theme_bw()
dev.off()




pwpp(em.test$emmeans, method = "pairwise")
```
There's no three way interaction (at least, we dont have the power to detect it), evidenced by the fact that the confidence intervals for estimated marginal means are virtually the same for each condition (tgt pos within a session) between orders (rand-struct and struct-rand). 

## a vs. a': Session * Position x Random Slope
```{r}
glm.less.slope <- glmer(rt_secs ~ sess * tgt_pos + 
                          (tgt_pos + sess | cond_order/subject), # correlated intercepts and slopes for tgt pos and sess
                        data = data, family = Gamma(link = "log"),
                        control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(glm.less.slope) 
  plot(resid(glm.less.slope))
  qqnorm(resid(glm.less.slope))
  Anova(glm.less.slope)
  save(glm.less.slope, file = "glm_less_slope.Rdata")
```
Model comparison penalizes the two models with random slopes. But try variants of the random effects model first. Note that it removed the singularity. 

## * RanEf Sess x Pos
```{r}
glm.less.slope1 <- glmer(rt_secs ~ sess * tgt_pos + (1 | cond_order/subject) + # intercept
                          (0 + tgt_pos | cond_order/subject), # uncorrelated slopes
                        data = data, family = Gamma(link = "log"),
                        control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(glm.less.slope1) 
  plot(resid(glm.less.slope1))
  qqnorm(resid(glm.less.slope1))
  Anova(glm.less.slope1)
  
glm.less.slope2 <- glmer(rt_secs ~ sess * tgt_pos + (1 | cond_order/subject) + # intercept
                          (0 + tgt_pos | cond_order/subject) +
                          (0 + sess | cond_order/subject), # uncorrelated slopes
                        data = data, family = Gamma(link = "log"),
                        control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(glm.less.slope2) 
  plot(resid(glm.less.slope2))
  qqnorm(resid(glm.less.slope2))
  Anova(glm.less.slope2)

# The winner is here!! 
glm.less.slope3 <- glmer(rt_secs ~ sess * tgt_pos + (1 | cond_order/subject) + # intercept
                          (0 + sess | cond_order/subject), # uncorrelated slopes for levels of session
                        data = data, family = Gamma(link = "log"),
                        control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(glm.less.slope3) 
  plot(resid(glm.less.slope3))
  qqnorm(resid(glm.less.slope3))
  Anova(glm.less.slope3)
  save(glm.less.slope3, file = "glm_less_slope_sessrand.Rdata")

anova(glm.less.int,glm.less.slope,glm.less.slope1,glm.less.slope2,glm.less.slope3)

```


```{r}
ranef(glm.less.slope)

ranef(glm.less.slope1)

ranef(glm.less.slope2)

ranef(glm.less.slope3)



dotplot(ranef(glm.less.slope))

dotplot(ranef(glm.less.slope1))

dotplot(ranef(glm.less.slope2))

dotplot(ranef(glm.less.slope3))


dotplot(glm.less.slope3, scales = list(x = list(relation = 'free')))[["subject:cond_order"]]

```

#### -> Save Regression Table Session x Position + (Session)
```{r}
stargazer(glm.less.slope3,
type="html",
out="4_td_mod_1.doc",
intercept.bottom = FALSE,
intercept.top = TRUE,
ci = TRUE, 
digits=2,
notes = "Fitted using Gamma distribution and log link function.",
model.names = FALSE,
object.names = FALSE,
#column.labels = c("lesser", "lesser (random slopes)","fuller"),
single.row = T,
title="Table S2. GLM Results",
align=TRUE, 
dep.var.labels=c("reaction time (s)"),
covariate.labels = c("Intercept(Pos 1/Rand)",
"Struct",
"Pos 2",
"Pos 3", 
"Struct:Pos 2",
"Struct:Pos 3"),
add.lines = list(c("Fixed Effects", "Session Order/Subject + Session"),
                 c("Fixed Effects Struct.", "Rand. Int. + Rand. Slope")))
```

### Contrasts
#### position within session
```{r}
# express out to 4 digits
options("scipen"=100, "digits"=4)

# Anova on model 
car::Anova(glm.less.slope3, type = 3)
car::Anova(glm.less.slope3, type = 2)

# Contrasts
(em.tgt_pos.sess <- emmeans(glm.less.slope3, specs = pairwise ~ tgt_pos|sess, adjust = "tukey", transform = "response"))

ps.contrasts = summary(pairs(emmeans(glm.less.slope3, ~ tgt_pos|sess)))

# Cohen's d: divide emmeans estimates by residual sd of generating model:
ps.contrasts$d = ps.contrasts$estimate / sigmaHat(glm.less.slope3)

pos.sess.c <- em.tgt_pos.sess$contrasts %>%
     summary(infer=TRUE) %>%
     cbind(.,ps.contrasts$d) %>%
     as.data.frame() 

pos.sess.c_out <- pos.sess.c %>%
  transmute("ordinal position" = contrast, 
        session = sess,
        estimate = round(estimate,digits = 3),
         SE = round(SE, digits =3),
        df = df,
         "lower CI" = round(asymp.LCL, digits = 3),
         "upper CI" = round(asymp.UCL, digits = 3), 
         "z ratio" = round(z.ratio, digits = 3),
         "p value" = round(p.value, digits = 3),
        "Cohen's d" = round(`ps.contrasts$d`,digits = 3))
  
  # add_column("s value" = round(-log2(pos.sess.c$p.value),digits = 3))


stargazer(pos.sess.c_out, 
          type = "html", 
          out = file.path(res_path,'tables',"4_pos_sess_con.doc"), summary = FALSE, rownames = FALSE)

plot(em.tgt_pos.sess, comparisons = TRUE)

emmip(glm.less.slope3, sess ~ tgt_pos) 

# --------------------- Uncorrected
# em.tgt_pos.sess.n <- emmeans(glm.less.slope3, specs = pairwise ~ tgt_pos|sess, adjust = "none", transform = "response")
```

#### session within position
```{r}
(em.sess.pos <- emmeans(glm.less.slope3, specs = pairwise ~ sess|tgt_pos, adjust = "tukey", transform = "response"))

sp.contrasts = summary(pairs(emmeans(glm.less.slope3, ~ sess|tgt_pos)))

# Cohen's d: divide emmeans estimates by residual sd of generating model:
sp.contrasts$d = sp.contrasts$estimate / sigmaHat(glm.less.slope3)

plot(em.sess.pos, comparisons = TRUE)

# --------------------- Uncorrected
# em.sess.pos.n <- emmeans(glm.less.slope3, specs = pairwise ~ sess|tgt_pos, adjust = "none", transform = "response")
```

```{r}
#png(file = file.path(fig_path,'fig6_int_pos_and_session.png'), width = w, height = h, res = 300, units = "in")
emmip(glm.less.slope3, tgt_pos ~ sess, xlab = "Condition", CIs = TRUE, type = "response") +  
  scale_y_continuous(name="Est. marginal means (s)") +
  scale_x_discrete(labels = c("random","structure")) +
  scale_color_brewer(name = "Position",palette="Dark2",guide = NULL) + 
  theme(text = element_text(family = "LM Roman 10", face="bold", size = 22))  
#dev.off()
```

## Fig. 3c. RT ~ Pos|Sess EM
```{r}
as.data.frame(em.sess.pos$emmeans)

# ggplot(as.data.frame(em.sess.pos$emmeans),aes(x=sess)) + 
#   geom_boxplot(
#     aes(y=response,color=tgt_pos,linetype=sess,
#                    lower = response-SE,
#                    middle = response,
#                    upper = response+SE,
#                    stat = "identity"))


ggplot(as.data.frame(em.sess.pos$emmeans),aes(x=sess,y=response)) + 
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL,color=tgt_pos,linetype=sess), position = position_dodge(width = 0.2)) + 
  geom_line(aes(group=tgt_pos,color=tgt_pos), position = position_dodge(width = 0.2)) + 
  scale_color_brewer(palette="Dark2",name="Position") + 
  scale_linetype_manual(guide = NULL,values = c("solid","dashed")) + 
  scale_y_continuous(name="Est. marginal means (s)") +
  scale_x_discrete(labels = c("random","structure"), name = "Condition") +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size=22),legend.position="top") +
  ggsave(file.path(fig_path,'fig3c_estimatedmeans.png'), width = w, height = h)

```

```{r}
require(ggplot2)
ggplot(data, aes(sess,rt,color = tgt_pos,linetype = sess)) + 
  geom_boxplot(outlier.shape = NA,varwidth=FALSE) +
  scale_color_brewer(palette="Dark2",name="Position") + 
  scale_linetype_manual(guide = NULL,values = c("solid","dashed"))
 # geom_line(aes(group = tgt_pos))
```

#### control: three-way int
```{r}
(em.test <- emmeans(glm.fuller.int, specs = pairwise ~ cond_order|sess*tgt_pos, adjust = "tukey", transform = "response"))
car::Anova(glm.fuller.int, type = "III")
em.test$contrasts %>%
     summary(infer=TRUE) %>%
     rbind() %>%
     as.data.frame()

plot(em.test, comparisons = TRUE)


#png(file = 'exp4figS2.png', width = w, height = h, res = 300, units = "in")
emmip(glm.fuller.int, tgt_pos*sess ~ cond_order, xlab = "session order", CIs = TRUE) +
  labs(color = "position") + 
  scale_color_brewer(palette = "Dark2") +
  #scale_color_manual(values = c(RColorBrewer::brewer.pal(3,"Dark2"),RColorBrewer::brewer.pal(3,"Pastel2"))) + 
  theme(legend.title = element_text(face = "bold")) + 
  theme_bw()
#dev.off()

```

## Contra Honey: Control
```{r}
data <- data %>% mutate(trial = as.factor(trial),target_num = as.factor(target_num))

check.lm.40 <- lm(rt ~ target_num, data)
summary(check.lm.40)
plot(resid(check.lm.40))
Anova(check.lm.40)

check.lm.4 <- lm(rt ~ target_num*sess, data)
summary(check.lm.4)
plot(resid(check.lm.4))
Anova(check.lm.4)

emmeans(check.lm.4, specs = pairwise ~ target_num*sess, adjust = "Tukey", transform = "response")
```

## Fig. S2d. Target Num * Sess
```{r}

ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num"),na.rm = TRUE)) +
  geom_smooth(aes(target_num,rt_median))

ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num","sess"),na.rm = TRUE)) +
  geom_smooth(aes(target_num,rt_median, group = sess, color = sess))

ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num","trial"),na.rm = TRUE)) +
  geom_smooth(aes(target_num,rt_median, group = trial)) + 
  facet_wrap(. ~ trial, nrow = 2)

ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num","trial","sess"),na.rm = TRUE)) +
  geom_smooth(aes(target_num,rt_median, group = sess, linteype = sess)) +
  facet_wrap(. ~ trial, nrow = 2)

ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num","sess","tgt_pos"),na.rm = TRUE)) +
  geom_smooth(aes(target_num,rt_median, group = tgt_pos, color = tgt_pos)) +
  facet_wrap(. ~ sess, nrow = 2)

ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num","trial","tgt_pos", "sess"),na.rm = TRUE)) +
  geom_smooth(aes(target_num,rt_median, group = tgt_pos, color = tgt_pos, linetype = sess)) +
  facet_wrap(. ~ trial, nrow = 2)



ggplot(data %>% summarySE(.,measurevar = "rt",groupvars = c("target_num","sess"),na.rm = TRUE)) +
  geom_point(aes(target_num,rt_mean), size = 2) +
  geom_line(aes(target_num,rt_mean, group = sess, linetype = sess)) + 
  geom_smooth(aes(target_num,rt_mean, group = sess, linetype = sess), color = "red") + 
  scale_y_continuous(name = "Mean RT (ms)") +
  scale_x_discrete(name = "Target number")  +
  #scale_color_brewer(palette = "Set1") + 
  scale_linetype_manual(name = "condition", values = c('solid', 'dashed')) + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold",size = 22), legend.position = "top") +
  ggsave(file.path(fig_path,'figs2c_tgt_num_exp4.png'), width = w, height = h)

```


## - Target Position
```{r}
# glm.e <- glmer(rt_secs ~ tgt_pos + (1 | cond_order/subject), data = data, family = Gamma)
#   summary(glm.e)
#   plot(glm.e)
#   qqnorm(resid(glm.e))
#   Anova(glm.e)
#   
# anova(glm.less.int,glm.e) # Go with a...
```

glm.lesser.int (factor session only) appears to win out in all model comparisons. For the sake of pursuing planned analyses, we will look at this one, but also glm.less.int (with session*target position as factors). 



## - Session
```{r}
# glm.lesser.int <- glmer(rt_secs ~ sess + (1 | cond_order/subject), data = data, family = Gamma(link = "log"),
#                         control = glmerControl(optimizer="bobyqa",
#                             optCtrl=list(maxfun=2e5)))
#   summary(glm.lesser.int)
#   plot(glm.lesser.int)
#   qqnorm(resid(glm.lesser.int)) # How to properly interpret this? 
#   Anova(glm.lesser.int)
# Notes: Fit is singular, session has a very siginficant effect, and subject and condition order account for negligible variance.
```

Contrasts: rand-struct
```{r}
# Source: https://aosmith.rbind.io/2019/03/25/getting-started-with-emmeans/
# Learn more about contrasts with emmeans.
# ?contrast.emmGrid
# ?`emmc-functions`
# ?`contrast-methods`
# Note that emmeans also supports glht function in the multcomp package

# (em.glm.lesser.int <- emmeans(glm.lesser.int, specs = pairwise ~ sess, adjust = "tukey", transform = "response"))
# 
# # Confidence Intervals
# em.glm.lesser.int.pairs <- em.glm.lesser.int$contrasts %>%
#     summary(infer=TRUE) # same as confint() but adds p-value
#      rbind() %>%
#      as.data.frame()
#      
# # blue bars are CI for emm, red bars are comparisons among them
# plot(em.glm.lesser.int, comparisons = TRUE)
# 
# pwpp(em.glm.lesser.int$emmeans, method = "pairwise")
# #https://rdrr.io/cran/emmeans/man/pwpp.html
# 
# emmip(glm.lesser.int, sess ~ sess, type = "response") 
# #https://rdrr.io/cran/emmeans/f/vignettes/messy-data.Rmd
# 
# # --------------------- Uncorrected
# 
# (em.glm.lesser.int_unc <- emmeans(glm.lesser.int, specs = pairwise ~ sess, adjust = "none", transform = "response"))
# 
# plot(em.glm.lesser.int_unc, comparisons = TRUE)
# 
# pwpp(em.glm.lesser.int_unc$emmeans, method = "pairwise")

```

## - Session * Condition Order
```{r}
# glm.b.i <- glmer(rt_secs ~ sess + cond_order + (1 | cond_order/subject), data = data, family = Gamma)
#   summary(glm.b.i)
#   plot(glm.b.i)
#   qqnorm(resid(glm.b.i))
#   Anova(glm.b.i)
#   
# anova(glm.lesser.int,glm.b.i)
# No true difference between these models... 

# glm.full.int <- glmer(rt_secs ~ sess * cond_order + (1 | cond_order/subject), data = data, family = Gamma(link = "log"))
#   summary(glm.full.int)
#   plot(resid(glm.full.int))
#   qqnorm(resid(glm.full.int))
#   Anova(glm.full.int)
#   # Note: an effect of session, but not order nor the interaction
# 
# anova(glm.lesser.int,glm.full.int)
# Again, no true difference...
```

# 5. Delta RTs
## Calculate
```{r}
# take the diff between median RTs to positions 1,2,3
# D1-2, D2-3, D1-3
options(scipen=999)
data_delta <- data_sum7 %>% 
  arrange(subject, sess,tgt_word) %>%
  group_by(subject,sess,tgt_word) %>%
  mutate(delta = rt_median - lead(rt_median,default=first(rt_median))) %>%
  mutate(delta = round(delta,digits=5))
#This works for 1-2 and 2-3, but for 3-1 it pulls the "1" not from the same group, but from the next item in the array. adding order_by as an argument in lead, leads it to pull from the next grouping factor (i.e. 1st item in struct-tgt_word 1 after rand-tgt_word 1)
data_delta <- data_delta %>%
    arrange(subject,sess,tgt_word) %>%
    group_by(subject,sess,tgt_word) %>%
    mutate(delta1.3 = rt_median - lead(rt_median,n=2)) %>%
    mutate(delta1.3 = data.table::shift(delta1.3,n=2))

vals.1.3 <- data_delta$delta1.3[which(data_delta$tgt_pos==3)]
data_delta$delta[which(data_delta$tgt_pos==3)] <- vals.1.3

data_delta <- data_delta[,-13]

data_delta <- data_delta %>%
 mutate(cond_order = 0) 
data_delta$cond_order[which(data_delta$subject %in% subjs_SR)] = "struct-rand"
data_delta$cond_order[which(data_delta$subject %in% subjs_RS)] = "rand-struct"

# Target positions should be recoded to delta 1-2, 2-3, 1-3 to avoid confusion. 
colnames(data_delta)[2] <- "delta_rt"
data_delta <- data_delta %>% 
  mutate(
    delta_rt = case_when(delta_rt==1 ~ "D1-2",
                         delta_rt==2 ~ "D2-3",
                         delta_rt==3 ~ "D1-3"))
data_delta <- data_delta %>% mutate(delta_rt = as.factor(delta_rt))
data_delta$delta_rt <- factor(data_delta$delta_rt, levels = c("D1-2", "D2-3", "D1-3"))


write.csv(data_delta,file.path(data_path,"exp_4_rt_data_delta.csv"), row.names = FALSE)
```

## Plot
Plot the mean of the differences between median RTs...
```{r}
data_sum9 <- data_delta %>%
    summarySE(measurevar="delta", groupvars=c("delta_rt","sess","tgt_word"), na.rm=TRUE)
data_sum10 <- data_delta %>%
    summarySE(measurevar="delta", groupvars=c("delta_rt","sess"), na.rm=TRUE)

ggplot() +
  geom_point(data = data_sum9, mapping = aes(x=delta_rt,y=delta_mean, colour = factor(tgt_word)), size = 2) +
  geom_line(data = data_sum9, mapping = aes(x = delta_rt, y = delta_mean, group = tgt_word), colour = "GREY",size = .5) +
  geom_point(data = data_sum10, mapping = aes(x = delta_rt, y = delta_mean), colour = "BLACK") +
  geom_errorbar(data = data_sum10, mapping = aes(x = delta_rt, y = delta_mean, ymin = delta_mean-se, ymax = delta_mean+se), colour = "BLACK", width = 0.1, size = 0.8) +
  geom_line(data = data_sum10, mapping = aes(x = delta_rt, y = delta_mean, group = 1), colour = "BLACK", size = .9) +
  facet_grid(~sess) +
  scale_colour_brewer(palette = "Paired") +
  labs(colour= "Trial (Word)") + ylab('Mean of Median Differences (ms) [bars = SEM]') + xlab(expression(Delta*"Target Position")) +
  scale_x_discrete(labels=c(expression(delta*"1-2"),expression(delta*"2-3"),expression(delta*"1-3"))) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) #+
 # ggsave('targetdetection_delta_means.png', width = w, height = h)


```

## Fit Dist
```{r}
deltas <- data_delta$delta[!is.na(data_delta$delta)]

# A
delta_z<-(deltas-mean(deltas))/sd(deltas) 
n_dist <- length(deltas)
qqnorm(delta_z, main = "RT QQ for Norm Dist.") ## drawing the QQplot
abline(0,1) 

# B
descdist(deltas, discrete = FALSE)
fit.norm.delta  <- fitdist(deltas, "norm")
summary(fit.norm.delta)
par(mfrow=c(2,2))
plot.legend <- c("normal")
denscomp(list(fit.norm.delta), legendtext = plot.legend)
cdfcomp (list(fit.norm.delta), legendtext = plot.legend)
qqcomp  (list(fit.norm.delta), legendtext = plot.legend)
ppcomp  (list(fit.norm.delta), legendtext = plot.legend)

shapiro.test(deltas) # marginally normal! it's fine.

```
The distribution is roughly normal. Proceed with gaussian fits. 

## Stats
```{r}
glm.deltas <- glmer(delta ~ sess * delta_rt + (1 | cond_order/subject), data = data_delta, family = gaussian)
  summary(glm.deltas)
  plot(glm.deltas)
  qqnorm(resid(glm.deltas))
  Anova(glm.deltas)
```

### Contrasts
```{r}
(em.deltas.sess <- emmeans(glm.deltas, specs = pairwise ~ delta_rt|sess, adjust = "tukey", transform = "response"))

em.deltas <- emmeans(glm.deltas, specs = pairwise ~ sess|delta_rt, adjust = "tukey", transform = "response")

em.deltas$contrasts 

em.deltas$emmeans 

em.deltas.pairs <- em.deltas$contrasts %>%
     summary(infer=TRUE) %>%
     rbind() %>%
     as.data.frame()

em.deltas.pairs$tgt_pos <- c("D1-2","D2-3","D1-3")
colnames(em.deltas.pairs)[2] <- "delta.rt"

plot(em.deltas, comparisons = TRUE)
```


