---
title: "RPSL - Study 3 - V2"
output: html_notebook
---

```{r}
rm(list=ls()) # clear workspace
# load(".RData") # load saved workspace image for this file

# Directories
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

# Data Path
data_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/1_data/exp_3'
# Code Path
code_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/2_code/exp_3'
# Results Path
res_path <- 'C:/Users/Ava/Desktop/Experiments/statistical_learning/3_results/exp_3'

```


Init.
```{r Initialize libraries, message=FALSE, include=FALSE}
# output
# library(knitr)
# library(Cairo)
#   opts_chunk$set(dev="CairoPDF")

# basics
library(tidyverse)
#library(reshape2)
#library(ggplot2)
#library(ggpubr)
#library(gplots)
library(fitdistrplus)

source('C:/Users/Ava/Desktop/Experiments/statistical_learning/2_code/summarySE.R')
source('C:/Users/Ava/Desktop/Experiments/statistical_learning/2_code/R_rainclouds.R')
  
# stats
library(lme4)
library(emmeans)

# save tables
library(stargazer)

# advanced plotting & stats  
#library(forcats)
#library(effects)
library(lsr) 
library(pwr)
library(RcppRoll) # for rolling means
library(car)

# latex font
library(extrafont)
  loadfonts(device = "win")
  par(family="LM Roman 10")
  
# colors
library("wesanderson")

# default figure size
w = 7
h = 5
```

Load
```{r Load data, message=FALSE, include=FALSE}
# 1. Online SL: Target Detection Task 

# IF YOU WISH TO PREPROCESS: LOAD THE ORIG FILE AND RUN CHUNKS UNDER
# 0 - PREPROCESING
# rt_data_orig <- read_csv(file.path(data_path,'RT_response_table.csv'))
# OTHERWISE, LOAD PREPROCESSED DATA: 
rt_data <- read_csv(file.path(data_path,'exp_3_rt_data.csv')) %>%
      mutate(subject = as.factor(subject),
           block = as.factor(block),
           target = as.factor(target),
           tgt_pos = as.factor(tgt_pos),
           tgt_word = as.factor(tgt_word))

# 2. Offline SL: Word Recognition Task
wordrec_data_orig <- read_csv(file.path(data_path,'wordrec_task_data.csv')) %>%
    dplyr::select(subj_id:zabetu) %>%
    mutate(subject = as.factor(subj_id), subj_id = NULL) %>% 
    dplyr::select(subject,prop_word_chosen:zabetu)

```

# --- Target Detection Task 
# 0 - PREPROCESSING
```{r Clean up data, eval=FALSE, include=FALSE}



# Add blocks
rt_data_clean <- rt_data_orig[which(rt_data_orig$code!=0),]
  n_meta_blocks <- max(rt_data_orig$block)/max(rt_data_orig$tgt_pos)
    meta_blocks <- array(rep(0,each=nrow(rt_data_clean)))
    meta_blocks[which(rt_data_clean$block %in% c(1,2,3))] <- 1
    meta_blocks[which(rt_data_clean$block %in% c(4,5,6))] <- 2
    meta_blocks[which(rt_data_clean$block %in% c(7,8,9))] <- 3
    meta_blocks[which(rt_data_clean$block %in% c(10,11,12))] <- 4
    meta_blocks[which(rt_data_clean$block %in% c(13,14,15))] <- 5
    meta_blocks[which(rt_data_clean$block %in% c(16,17,18))] <- 6
    meta_blocks[which(rt_data_clean$block %in% c(19,20,21))] <- 7
    meta_blocks[which(rt_data_clean$block %in% c(22,23,24))] <- 8
  rt_data_clean <- add_column(rt_data_clean, meta_blocks, .after = 2)
  
# Rename & factorize columns
rt_data_cleaned.1 <- rt_data_clean %>% 
                     dplyr::select(2:6,8:11) %>%
                     dplyr::rename(subject = subjID, trial = block, block = meta_blocks, target_num = code, target = target_syll) %>%
                     mutate(subject = as.factor(subject),
                            block = as.factor(block),
                            target = as.factor(target), 
                            tgt_pos = as.factor(tgt_pos), 
                            tgt_word = as.factor(tgt_word),
                           # detect = case_when(detect==1 ~ 0,
                           #           detect==2 ~ 1),
                            detect = as.numeric(detect))



```
```{r Remove data with technical errors, eval=FALSE, include=FALSE}
rm_subjs <- c("b2308", # Did not respond at all
              "b1912","r1028", "t0204", # Trials were not blocked, so block numbers meaningless.
              "d2006", # Blocking messed up and didn't see all sylls; Block 6 = Target Positions 3,2,3; Blocks seen =  1-16, 1-8
              "i0902") # Blocking technically ok, just didn't see all syllables; Blocks seen = 1-12 x 2

rt_data_cleaned.2 <- rt_data_cleaned.1[which(!rt_data_cleaned.1$subject %in% rm_subjs),]
  
print(paste0("Of the original ", length(unique(rt_data_cleaned.1$subject)), " subjects, ", length(unique(rt_data_cleaned.2$subject)), " remain after removing participants with technical errors."))
  
```
```{r Visualize RT distributions/histograms, eval=FALSE, warning=FALSE, include=FALSE}
# view
hist(rt_data_cleaned.2$rt)
summary(rt_data_cleaned.2$rt)

rts <- rt_data_cleaned.2$rt %>% na.omit() %>% as.numeric()

descdist(rts, discrete = FALSE)
descdist(rts, discrete = FALSE, boot = 500)
# Distribution is gamma/lognormal.
```
```{r Compare fits to RT data, eval=FALSE, warning=FALSE, include=FALSE}
fit.gam  <- fitdist(rts, "gamma")
fit.ln <- fitdist(rts, "lnorm")
summary(fit.gam)
summary(fit.ln)

par(mfrow=c(2,2))
plot.legend <- c("gamma", "lognorm")
denscomp(list(fit.gam, fit.ln), legendtext = plot.legend)
cdfcomp (list(fit.gam, fit.ln), legendtext = plot.legend)
qqcomp  (list(fit.gam, fit.ln), legendtext = plot.legend)
ppcomp  (list(fit.gam, fit.ln), legendtext = plot.legend)

gofstat(list(fit.gam, fit.ln), fitnames = c("gamma", "lognorm"))
# Gamma distribution fits best. 
```
```{r Outlier removal, eval=FALSE, warning=FALSE, include=FALSE}
# Outlier Removal Method: median +- 3(mad) 
# --> https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/mad
# calculate
mad_norm <- mad(rt_data_cleaned.2$rt,na.rm=TRUE)
upper_bound_med <- median(rt_data_cleaned.2$rt,na.rm=TRUE)+(3*mad_norm)
lower_bound_med <- median(rt_data_cleaned.2$rt,na.rm=TRUE)-(3*mad_norm)

# filter & add scaled variables
rt_data <- rt_data_cleaned.2 %>%
  dplyr::filter(rt > lower_bound_med | is.na(rt), # keeps NAs, because these are miss markers
         rt < upper_bound_med | is.na(rt)) %>%
  mutate(rt_secs = rt/1000,
         rt_sc = scale(rt))

# replot
rts.rm <- rt_data$rt %>% na.omit() %>% as.numeric()
hist(rts.rm)
descdist(rts.rm, discrete = FALSE)

fit.norm <- fitdist(rts.rm, "norm")
fit.gam  <- fitdist(rts.rm, "gamma")
fit.ln <- fitdist(rts.rm, "lnorm")
summary(fit.norm)
summary(fit.gam)
summary(fit.ln)

par(mfrow=c(2,2))
plot.legend <- c("norm","gamma", "lognorm")
denscomp(list(fit.norm,fit.gam, fit.ln), legendtext = plot.legend)
cdfcomp (list(fit.norm,fit.gam, fit.ln), legendtext = plot.legend)
qqcomp  (list(fit.norm,fit.gam, fit.ln), legendtext = plot.legend)
ppcomp  (list(fit.norm, fit.gam, fit.ln), legendtext = plot.legend)

gofstat(list(fit.norm, fit.gam, fit.ln), fitnames = c("norm","gamma", "lognorm"))

print(paste0("The method of removing +- 3 * the median absolute deviation results in a data loss of only ", round(1-length(rt_data$rt)/length(rt_data_cleaned.2$rt), digits = 3), "%. Meanwhile, although outlier removal makes the distribution much more normal (note scaling does not add any further normality), gamma remains the best fit."))
```
```{r Summary statistics before/after outlier removal, eval=FALSE, include=FALSE}
summary(sort(rts))
summary(sort(rts.rm))
```
```{r Rescale response variable, eval=FALSE, include=FALSE}
# rescale y var
rt_data <- rt_data %>%
   mutate(rt_secs = rt/1000)
```
```{r Save data, eval=FALSE, include=FALSE}
write.csv(rt_data,'exp_3_rt_data.csv', row.names = FALSE)
```
```{r}
hist(rt_data$rt)
summary(rt_data$rt)
count(sort(rt_data$rt) < 100)


```

# 1 - PLOTS
## Fig. 1a. Plot RT ~ Pos x Block 
```{r message=FALSE, warning=FALSE}
rt_data_sum1 <- rt_data %>% # target position x block
    summarySE(measurevar = "rt", groupvars = c("block","tgt_pos"),na.rm=TRUE) 
rt_data_sum2 <- rt_data %>% # target position only
    summarySE(measurevar = "rt", groupvars = c("tgt_pos"),na.rm=TRUE)
  
ggplot() +
 # geom_point(data = rt_data_sum1, mapping = aes(x=tgt_pos,y=rt_median, colour = factor(block)), size = 2) +
#  geom_line(data = rt_data_sum1, mapping = aes(x = tgt_pos, y = rt_median, group = block, colour = factor(block)),size = .5) +
  geom_point(data = rt_data_sum2, mapping = aes(x = tgt_pos, y = rt_median), colour = "BLACK") +
  geom_errorbar(data = rt_data_sum2, mapping = aes(x = tgt_pos, y = rt_median, ymin = rt_median-ci, ymax = rt_median+ci), colour = "BLACK", width = 0.1, size = 0.8) +
  geom_line(data = rt_data_sum2, mapping = aes(x = tgt_pos, y = rt_median, group = 1), colour = "BLACK", size = .9) +
  
  scale_colour_brewer(palette = "Paired") +
  scale_y_continuous(limits=c(380,580)) +
  #  annotate("text", x = 3.4, y = 570, label = paste("N =",toString(N))) +
  #labs(colour= "Block") + 
  ylab('Median Response Time (ms) [bars = CI]') + xlab('Target Postion') +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
#  ggsave(file.path(res_path,'figures','fig1a_rt_pos_block.png'), width = w, height = h)
  ggsave(file.path(res_path,'figures','fig1a_rt_pos_avg.png'), width = w, height = h)

# dev.copy(pdf,file.path(res_path,'figures','fig1artposblock.pdf'), width = 6, height = 4)
# dev.off()
```

## Fig. 1b. Plot RT ~ Pos (Raincloud)
```{r message=FALSE, warning=FALSE}
rt_data_sum3 <- rt_data %>% # target position x subject
    summarySE(measurevar = "rt", groupvars = c("tgt_pos","subject"),na.rm=TRUE)
    
ggplot(rt_data_sum3, aes(x = tgt_pos, y = rt_median, fill = tgt_pos)) +
  geom_point(position = position_jitter(width = .07)) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 1, trim = FALSE) + 
  geom_boxplot(width = 0.1, alpha = 0.5, position = position_nudge(x=0.2,y=0)) +
  #scale_fill_manual(values=wes_palette("Royal2")[c(3,4,5)]) +
  scale_color_brewer(palette="Dark2") + 
  scale_fill_brewer(palette="Pastel2") +
#  scale_y_continuous(limits=c(380,580)) +
  ylab('Median Response Time (ms) [bars = CI]') + xlab('Target Postion') +
  guides(fill = FALSE, color = FALSE) + 
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggsave(file.path(res_path,'figures','fig1b_rt_pos.png'), width = w, height = h)
dev.copy(pdf,file.path(res_path,'figures','fig1b.pdf'), width = 6, height = 4)
dev.off()
```


## Fig. 2. Plot RT ~ Pos x Block x Subject
```{r message=FALSE, warning=FALSE}
rt_data_sum4 <- rt_data %>% # target position x block x subject
    summarySE(measurevar = "rt", groupvars = c("block","tgt_pos","subject"),na.rm=TRUE) 

ggplot(rt_data_sum4, mapping=aes(x=tgt_pos,y=rt_median,color=as.factor(block))) + 
  geom_point(size=1) +
  geom_line(aes(group=block), size=.5) +
  geom_point(rt_data_sum3, mapping=aes(x=tgt_pos,y=rt_median), color="BLACK") +
  geom_line(rt_data_sum3, mapping=aes(x=tgt_pos,y=rt_median,group=1), color="BLACK") +
  geom_errorbar(rt_data_sum3, mapping=aes(x=tgt_pos,y=rt_median,ymin=rt_median-ci,ymax=rt_median+ci), color="BLACK",width=.3) +
  
  ylab('Median Response Time (ms) [bars = CI]') + xlab('Target Postion') + labs(color="Block") +
  scale_color_brewer(palette="Paired") + 
  facet_wrap(. ~ subject, ncol=7) +
  theme_bw() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggsave(file.path(res_path,'figures','fig2_rt_pos_block_subj.png'),width=18,height=14)
dev.copy(pdf,file.path(res_path,'figures','exp3fig2.pdf'))
dev.off()

```
## Fig. 3a. Rolling Average RT
```{r warning=FALSE, include=FALSE}
# There are 18 targets per block. 3 blocks in each block (set of trials where all 3 positions serve as targets). 
# We can have a moving average spanning 3 items...
rt_data_roll <- subset(rt_data, select = c("subject","block", "trial", "target_num", "tgt_pos", "rt"))
rt_data_rolled <- data.frame(subject = factor(),
                             block = factor(),
                             trial = numeric(),
                             target_num = numeric(),
                             tgt_pos = factor(),
                             rt = numeric(),
                             moving_mean = numeric(),
                             stringsAsFactors = FALSE)
# calculate rolling average for each subject and each block (so that averages don't include observations from unrelated groups)
for (subj in unique(rt_data_roll$subject)) {
  curr_subj <- rt_data_roll %>%
    filter(subject == subj) 
  for (blk in unique(curr_subj$block)) {
    curr_roll <- curr_subj %>%
    filter(block == blk) %>%
    mutate(moving_mean = roll_mean(rt, 3, align = "right", fill = NA, na.rm = TRUE)) %>%
    filter(!is.na(rt))
    rt_data_rolled <- bind_rows(rt_data_rolled,curr_roll)} 
   }
#view(rt_data_rolled)

# make the first two values in the moving mean column for each block simply the 1st and 2nd RT value
rt_idx <- sort(c(which(rt_data_rolled$target_num==1),which(rt_data_rolled$target_num==2)))
rt_data_rolled$moving_mean[rt_idx] <- rt_data_rolled$rt[rt_idx]

# group over subjects
rolled_over_subjs_blocks <- rt_data_rolled %>%
  filter(!is.na(moving_mean)) %>%
  summarySE(measurevar = "moving_mean",groupvars = c("tgt_pos","target_num"), na.rm = TRUE)
```

```{r warning=FALSE}


#ggplot(rolled_over_subjs_blocks[rolled_over_subjs_blocks$target_num %in% seq(1,18,2),], mapping=aes(target_num,moving_mean_mean,colour=tgt_pos)) +
ggplot(rolled_over_subjs_blocks, mapping=aes(target_num,moving_mean_mean,colour=tgt_pos)) +
    geom_point() +
  geom_line(aes(group=tgt_pos)) +
  geom_ribbon(aes(x=target_num,ymin=moving_mean_mean-se,ymax=moving_mean_mean+se,fill=tgt_pos),alpha=.2) +
    scale_x_discrete(limits=c(1:18),name="Occurrence of target syllable") + 
#    scale_x_discrete(limits=seq(1,18,2),name="Occurrence of target syllable") + 
  scale_y_continuous(name="Mean RT [shaded = SEM]", ) +
  scale_color_brewer(palette="Dark2", name = "Target Position",
                     labels = c("1st","2nd","3rd")) + 
  scale_fill_brewer(palette="Pastel2", guide = FALSE) +
  # scale_fill_manual(values=wes_palette("Royal2")[c(3,4,5)], guide = FALSE) +
  # scale_color_manual(values=wes_palette("Royal2")[c(3,4,5)], 
  #                    name = "Target Position",
  #                    labels = c("1st","2nd","3rd")) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), legend.position = "top") +
  ggsave(file.path(res_path,'figures','fig3_rt_rolling.png'), width = w, height = h)
dev.copy(pdf,file.path(res_path,'figures','exp3fig3rolling.pdf'), width = w, height = h)
dev.off()
```
Impressively, only a few exposures to the words are enough for participants' reaction times to differentiate syllables based on their position.

## Fig. 3b. Plot Blocks as Facets
```{r}
rolled_over_subjs <- rt_data_rolled %>%
  filter(!is.na(moving_mean)) %>%
  summarySE(measurevar = "moving_mean",groupvars = c("tgt_pos","target_num","block"), na.rm = TRUE)

ggplot(rolled_over_subjs[rolled_over_subjs$target_num %in% seq(1,18,3),], mapping=aes(target_num,moving_mean_mean,colour=tgt_pos)) +
#ggplot(rolled_over_subjs, mapping=aes(target_num,moving_mean_mean,colour=tgt_pos)) +
    geom_point(size=1) +
    geom_line(aes(group=tgt_pos)) +
  geom_ribbon(aes(x=target_num,ymin=moving_mean_mean-se,ymax=moving_mean_mean+se,fill=tgt_pos),alpha=.2) +
  xlab("Occurrence of target syllable") + 
  ylab("Mean RT [shaded = SEM]") + 
#  scale_x_discrete(limits = c(1:18)) + 
  scale_x_discrete(limits = seq(1,18,3)) + 
  scale_color_brewer(palette="Dark2", name = "Target Position",
                     labels = c("1st","2nd","3rd")) + 
  scale_fill_brewer(palette="Pastel2", guide = FALSE) +
  # scale_fill_manual(values=wes_palette("Royal2")[c(3,4,5)], guide = FALSE) +
  # scale_color_manual(values=wes_palette("Royal2")[c(3,4,5)], 
  #                    name = "Target Position",
  #                    labels = c("1st","2nd","3rd")) +
  facet_wrap(.~ block, ncol=4) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), legend.position = "top") +
  ggsave(file.path(res_path,'figures','fig3b_rt_rolling_smooth3.png'),width=14,height=10)
# dev.copy(pdf,file.path(res_path,'figures','exp3fig3brollingsmooth3.pdf'), width = 12, height = 10)
# dev.off()

```





# 2 - MODELS
```{r}
rt_data %>% summarySE(., measurevar = "rt_secs", groupvars = c("tgt_pos"), na.rm = TRUE)
```

## GLMM: RT ~ Pos x Block
### Fuller 
```{r}
options(contrasts = c("contr.sum", "contr.poly"))

# LOAD THE MODEL ALREADY RUN
load(file.path(res_path,'models','rt_block_full_int.Rdata'))

# Full Model | Random Intercept Only | Block as Factor | Gamma-log function
# rt.mod.full.int.fct <- glmer(rt_secs ~ 1 + tgt_pos*block + (1 | subject), data = rt_data, family = Gamma(link = "log"), control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(rt.mod.full.int.fct)
  plot(residuals(rt.mod.full.int.fct))
  qqnorm(resid(rt.mod.full.int.fct))
  Anova(rt.mod.full.int.fct, type = 2)
  anova(rt.mod.full.int.fct)
  # save(rt.mod.full.int.fct, file = file.path(res_path,'models','rt_block_full_int.Rdata'))

```

### *Lesser
```{r}
# Lesser Model | Random Intercept Only | Gamma-log function

load(file.path(res_path,'models','rt_block_less_int.Rdata'))

 # rt.mod.less.int <- glmer(rt_secs ~ 1 + tgt_pos + (1 | subject), data = rt_data, family = Gamma(link = "log"), control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(rt.mod.less.int)
  plot(residuals(rt.mod.less.int))
  qqnorm(resid(rt.mod.less.int))
  Anova(rt.mod.less.int,type = 2)
  anova(rt.mod.less.int)
 # save(rt.mod.less.int, file = file.path(res_path,'models','rt_block_less_int.Rdata'))
```

#### Effect Size
```{r}
pwr.chisq.test(w =, N = 33, df = 2, sig.level = 0.5, power = )



```



#### Model Evaluation
```{r}
anova(rt.mod.full.int.fct,rt.mod.less.int) 
```
There is a small but significant difference in the fit of the two models. The lesser model is the one we'll continue with, but we will still explore the effect of block. 

Models with a delta AIC of greater than 10 suggest almost no support for the fuller model. For more info, see here: https://stats.stackexchange.com/questions/232465/how-to-compare-models-on-the-basis-of-aic


### Full, Lesser | Random Slopes 
```{r}
load(file.path(res_path,'models','rt_block_full_slope.Rdata'))
#rt.mod.full.int.slope <- glmer(rt_secs ~ 1 + tgt_pos*block + (tgt_pos | subject), data = rt_data, family = Gamma(link = "log"), control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  summary(rt.mod.full.int.slope)
  plot(residuals(rt.mod.full.int.slope))
  qqnorm(resid(rt.mod.full.int.slope))
 #save(rt.mod.full.int.slope, file = file.path(res_path,'models','rt_block_full_slope.Rdata'))

load(file.path(res_path,'models','rt_block_less_slope.Rdata'))
#rt.mod.less.int.slope <- glmer(rt_secs ~ 1 + tgt_pos + (tgt_pos | subject), data = rt_data, family = Gamma(link = "log"))
  summary(rt.mod.less.int.slope)
  plot(residuals(rt.mod.less.int.slope))
  qqnorm(resid(rt.mod.less.int.slope))
 # save(rt.mod.less.int.slope, file = file.path(res_path,'models','rt_block_less_slope.Rdata'))

# Eval  
anova(rt.mod.less.int,rt.mod.full.int.slope,rt.mod.less.int.slope)
```
Again, the lesser, random intercepts model is a better description of the data, by AIC value. 

A final comparison, by testing if allowing random slopes for both position and block per subject is a better reflector than only for target position. 

```{r Output regression table., include=FALSE}
stargazer(rt.mod.less.int, rt.mod.less.int.slope, rt.mod.full.int.fct,
type="html",
out=file.path(res_path,'tables','td_mods.doc'),
intercept.bottom = FALSE,
intercept.top = TRUE,
ci = TRUE, 
digits=2,
notes = "Fitted using Gamma distribution and log link function.",
model.names = FALSE,
object.names = FALSE,
column.labels = c("lesser", "lesser (random slopes)","fuller"),
single.row = T,
title="Table 1. GLM Results",
align=TRUE, 
dep.var.labels=c("reaction time (s)"),
covariate.labels = c("Intercept(Pos 1)",
"Pos 2",
"Pos 3", 
"Block 2",
"Block 3",
"Block 4",
"Block 5",
"Block 6",
"Block 7",
"Block 8",
"Pos 2:Block 2",
"Pos 3:Block 2",
"Pos 2:Block 3",
"Pos 3:Block 3",
"Pos 2:Block 4",
"Pos 3:Block 4",
"Pos 2:Block 5",
"Pos 3:Block 5",
"Pos 2:Block 6",
"Pos 3:Block 6",
"Pos 2:Block 7",
"Pos 3:Block 7",
"Pos 2:Block 8",
"Pos 3:Block 8"),
add.lines = list(c("Fixed Effects", "Subject", "Position | Subject", "Subject"),
                 c("Fixed Effects Struct.", "Rand. Int.", "Rand. Int., Slope", "Rand Int.")))


```

### Lesser | Random Slopes for both Factors
```{r}
#load(file.path(res_path,'models','rt_block_less_slope2.Rdata'))
rt.mod.less.int.slope2 <- glmer(rt_secs ~ 1 + tgt_pos + (tgt_pos | subject) + (block | subject), data = rt_data, family = Gamma(link = "log"), control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(rt.mod.less.int.slope2)
plot(residuals(rt.mod.less.int.slope2))
qqnorm(resid(rt.mod.less.int.slope2))
save(rt.mod.less.int.slope2, file = file.path(res_path,'models','rt_block_less_slope2.Rdata'))

# Model comparison
anova(rt.mod.less.int,rt.mod.less.int.slope,rt.mod.less.int.slope2)
```
Yet again, go for the simplest model. 


## Contrasts 
```{r}
(emm.pos <- emmeans(rt.mod.less.int, specs = pairwise ~ tgt_pos, adjust = "tukey", transform = "response"))

p.contrasts = summary(pairs(emmeans(rt.mod.less.int, ~ tgt_pos)))

# Cohen's d: divide emmeans estimates by residual sd of generating model:
p.contrasts$d = p.contrasts$estimate / sigmaHat(rt.mod.less.int)


position_contrasts <- emm.pos$contrasts %>%
  rbind() %>%
  as.data.frame() %>%
  cbind(CI.low = 
    emm.pos$contrasts %>% confint() %>% as.data.frame() %>% dplyr::select(asymp.LCL) %>% remove_rownames(),
             CI.hi = 
    emm.pos$contrasts %>% confint() %>% as.data.frame() %>% dplyr::select(asymp.UCL) %>% remove_rownames())

position_contrasts_out <- position_contrasts %>%
  transmute("ordinal position" = contrast,
         estimate = round(estimate,digits = 3),
         SE = round(SE, digits =3),
         "lower CI" = round(asymp.LCL, digits = 3),
         "upper CI" = round(asymp.UCL, digits = 3), 
         "z ratio" = round(z.ratio, digits = 3),
         "p value" = "<.001") %>%
  add_column("s value" = round(-log2(position_contrasts$p.value),digits = 3))

stargazer(position_contrasts_out, 
          type = "html", 
          out = file.path(res_path,'tables','td_mod_cont.doc'), summary = FALSE, rownames = FALSE)
```

```{r Explore Coefficients}
# library(broom)
# tidy(rt.mod.less.int,conf.int=TRUE) %>% as_tibble()
# # all fit values
# glance(rt.mod.less.int)
# # plot estimates
# tidy(rt.mod.less.int,conf.int=TRUE) %>% as_tibble() %>% 
#   .[c(1:3),] %>%
#   ggplot(aes(term, estimate, ymin=conf.low, ymax=conf.high)) +
#   geom_pointrange() +
#   geom_hline(yintercept = 0) 
# 
# # augment pulls out the fitted estimate and the residuals for all observations
# augment(rt.mod.less.int) %>%
#    ggplot(aes(x=.fitted, y=.resid)) +
#   geom_point() +
#   geom_smooth()  

```

## Fig. 1c. & S1 Contrasts: RT ~ Pos
```{r}
# Predicted Contrasts
png(file = file.path(res_path,'figures','fig1c.png'), width = w, height = h, res = 300, units = "in")
plot(emm.pos, comparisons = TRUE,
     xlab = "estimated marginal means",
     ylab = "ordinal position of target syllable") +
  theme_bw()
#dev.copy(pdf,file.path(res_path,'figures','fig1c.pdf'), width = 6, height = 4)
dev.off()

# Predicted Values
png(file = file.path(res_path,'figures','figS1.png'), width = w, height = h, res = 300, units = "in")
emmip(rt.mod.less.int, ~ tgt_pos, xlab = "Target Position", CIs = TRUE) +
  theme_bw()
#dev.copy(pdf,file.path(res_path,'figures','figS1.pdf'), width = 6, height = 4)
dev.off()

```

## Contrasts Con't (Pos x Block)
```{r}
# anova(rt.mod.full.int.fct,rt.mod.full.int.slope, rt.mod.full.int.slope2)
# Test showing that the full model with random intercepts only is the best fitting ^... 
(emm.pos.block <- emmeans(rt.mod.full.int.fct, specs = pairwise ~ tgt_pos|block, adjust = "tukey", transform = "response"))

block_contrasts <- emm.pos.block$contrasts %>%
  confint() %>%
  rbind() %>%
  as.data.frame() 

```

### Fig. S2. Contrasts: RT ~ Pos x Block
```{r}
plot(emm.pos.block, comparisons = TRUE,
     xlab = "estimated marginal means",
     ylab = "ordinal position of target syllable") +
   theme_bw() 
dev.copy(pdf,file.path(res_path,'figures'),'exp3figS2a.pdf'), width = 6, height = 4)
dev.off()

emmip(rt.mod.full.int.fct, tgt_pos ~ block, CIs = TRUE, xlab = "Block") +
  theme_bw() +
  scale_color_manual(name = "Position",
                     values=wes_palette("Royal2")[c(5,4,3)]) 
dev.copy(pdf,file.path(res_path,'figures','exp3figS2b.pdf'), width = 6, height = 4)
dev.off()

emmip(rt.mod.full.int.fct, block ~ tgt_pos, CIs = TRUE, xlab = "Target Position") + 
    theme_bw() + 
    scale_color_manual(name="block",
                 values=RColorBrewer::brewer.pal(8,"Paired"))
dev.copy(pdf,file.path(res_path,'figures','exp3figS2c.pdf'), width = 6, height = 4)
dev.off()
```


## Rolling Average GLMM
```{r}

rolled_over_subjs

```


## Block Contrasts
```{r}
Anova(rt.mod.full.int.fct)
emmeans(rt.mod.full.int.fct, specs = pairwise ~ block, adjust = "Tukey", transform = "response")



(within.em <- emmeans(rt.mod.full.int.fct, specs = pairwise ~ tgt_pos|block, adjust = "Tukey", transform = "response"))
# Drop in RT between 1-2 and 1-3 present in all blocks, 2-3 present in all but 3


contrasts1.2 <- within.em$contrasts %>%
  as.data.frame() %>%
  filter(contrast=="1 - 2")


contrasts1.3 <- within.em$contrasts %>%
  as.data.frame() %>%
  filter(contrast=="1 - 3")


t.test(contrasts1.2,)

within.em$contrasts %>%
  as.data.frame() %>%
  filter(contrast=="2 - 3")

emmeans(rt.mod.full.int.fct, specs = pairwise ~ block|tgt_pos, adjust = "Tukey", transform = "response")



```


```{r}

block.matters <- rt_data_sum4 %>%
  dplyr::select(subject, block, tgt_pos, rt_mean) %>%
  spread(tgt_pos, rt_mean) %>% 
  mutate(c1.2 = `1`-`2`,
         c1.3 = `1`-`3`,
         c2.3 = `2`-`3`)


# Is 1-2, 1-3, or 2-3 different between blocks? 

c1.2.mod <- lm(c1.2 ~ block, block.matters)
Anova(c1.2.mod)
emmeans(c1.2.mod, specs = pairwise ~ block, transform = "response", adjust = "Tukey")
# > mean(1)-mean(2) is not sig. different between blocks 

c1.3.mod <- lm(c1.3 ~ block, block.matters)
Anova(c1.3.mod)
emmeans(c1.3.mod, specs = pairwise ~ block, transform = "response", adjust = "Tukey")
# > none.

c2.3.mod <- lm(c2.3 ~ block, block.matters)
Anova(c2.3.mod)
emmeans(c2.3.mod, specs = pairwise ~ block, transform = "response", adjust = "Tukey")
# > none. 

```


# Regress out syllable effect
```{r}
# across all participants, median RTs for each of the syllables
# rm anova with syllable and position as factors
subj.mod <- glmer(rt ~ tgt_pos*target + (1 | subject), data = rt_data, family = Gamma("log"), control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(subj.mod)
# for each participant, subtracted the residual RT value from observed value for each syllable, co-varying out the effects of physical stimulus factors and yielding corrected RT effect

# Model is rank-deficient

library(broom)
broom::glance(subj.mod)
augment(subj.mod)
rt_data_adj <- data.frame(subject = as.factor(augment(subj.mod)$subject),
           tgt_pos = as.factor(augment(subj.mod)$tgt_pos),
           rt_adj = as.numeric(augment(subj.mod)$rt - augment(subj.mod)$.resid))
         
rt.mod.less.int.adj <- glmer(rt_adj ~ 1 + tgt_pos + (1 | subject), data = rt_data_adj, family = Gamma(link = "log"))
  summary(rt.mod.less.int.adj)
  plot(residuals(rt.mod.less.int.adj))
  qqnorm(resid(rt.mod.less.int.adj))
  
  car::Anova(rt.mod.less.int.adj)
```



# 3 - ACCURACY STATS
### Stats
```{r}
rt_data %>%
  summarise(mean = mean(detect),
            sd = sd(detect))
individ_mean <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("subject"),na.rm=TRUE) 
t.test(individ_mean$detect_mean, alternative = "greater", mu = 0.5)

rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos"),na.rm=TRUE) 
rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_word"),na.rm=TRUE) 
rt_data %>% summarySE(measurevar = "detect", groupvars = c("target"),na.rm=TRUE) 

#---- Position
# Linear Model
acc.mod.less <- lm(detect ~ tgt_pos, rt_data)
summary(acc.mod.less)
Anova(acc.mod.less)
# Contrasts
(em.acc.less <- emmeans(acc.mod.less, specs = pairwise ~ tgt_pos, adjust = "tukey", transform = "response"))
# Plot Interactions
plot(em.acc.less, comparisons = TRUE,
     xlab = "estimated marginal means (accuracy)",
     ylab = "ordinal position of target syllable") +
  theme_bw()

#---- Word
# Linear Model
acc.mod.less2 <- lm(detect ~ tgt_word, rt_data)
summary(acc.mod.less2)
Anova(acc.mod.less2)
# Contrasts
(em.acc.less2 <- emmeans(acc.mod.less2, specs = pairwise ~ tgt_word, adjust = "tukey", transform = "response"))
# Plot Interactions
plot(em.acc.less2, comparisons = TRUE,
     xlab = "estimated marginal means (accuracy)",
     ylab = "word of target syllable") +
  theme_bw()

#---- Syllable
# Linear Model
acc.mod.less3 <- lm(detect ~ target, rt_data)
summary(acc.mod.less3)
Anova(acc.mod.less3)
# Contrasts
(em.acc.less3 <- emmeans(acc.mod.less3, specs = pairwise ~ target, adjust = "tukey", transform = "response"))
# Plot Interactions
plot(em.acc.less3, comparisons = TRUE,
     xlab = "estimated marginal means (accuracy)",
     ylab = "target syllable") +
  theme_bw()



```
Now: Accuracy of 0.70 and sd of 0.45.
Previously: Average accuracy is 0.73 with an SD of 0.26. Precision (true positives/true + false positives) is at 0.80 with an SD of 0.23. 


### a. Accuracy per position
```{r}
#[did i accidentally delete it?]

accuracy_data1 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos","subject"),na.rm=TRUE) 
accuracy_data2 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos"),na.rm=TRUE)

#------ Averaged Data
pos.lm <- lm(detect_mean ~ tgt_pos, accuracy_data1)
    summary(pos.lm)
    Anova(pos.lm, type = '2')
    (emmeans(pos.lm, specs = pairwise ~ tgt_pos))
```

## Fig. 4. Accuracy: RT ~ Pos
```{r}
accuracy_data1 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos","subject"),na.rm=TRUE) 
accuracy_data2 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos"),na.rm=TRUE) 

# Boxplot
# ggplot(accuracy_data2) + 
#   geom_col(mapping=aes(tgt_pos, detect_mean, fill= (tgt_pos)), 
#            position = position_dodge(0.5), width=0.5) +
#   geom_errorbar(mapping=aes(tgt_pos, y=detect_mean, ymin=detect_mean-se, ymax=detect_mean+se,
#            group=tgt_pos,color=tgt_pos), position=position_dodge(0.5), width = 0.3, size = 1) +
#   scale_y_continuous(limits = c(0,1), name = "mean detection accuracy [bars = SEM]") +
#   scale_x_discrete(name = "Target Position") + 
#   scale_color_brewer(palette="Dark2") + 
#   scale_fill_brewer(palette="Pastel2") +
#   guides(fill=FALSE, color = FALSE) +
#   theme_minimal() +
#   theme(text = element_text(family = "LM Roman 10", face="bold")) +
#   ggsave(file.path(res_path,'figures','fig4_rt_acc.png'),width=w,height=h)

# Raincloud
ggplot(accuracy_data1, aes(x = tgt_pos, y = detect_mean, fill = tgt_pos)) +
  geom_point(position = position_jitter(width = .07)) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 1, trim = FALSE) + 
  geom_point(accuracy_data2, mapping = aes(tgt_pos, detect_mean), position = position_nudge(x = 0.2, y = 0)) +
  geom_errorbar(accuracy_data2, mapping=aes(tgt_pos, y=detect_mean, ymin=detect_mean-se,
                                            ymax=detect_mean+se),
                position = position_nudge(x = 0.2, y = 0), width = 0.05, size = 1) +
  #scale_fill_manual(values=wes_palette("Royal2")[c(3,4,5)]) +
  scale_color_brewer(palette="Dark2") + 
  scale_fill_brewer(palette="Pastel2") +
  scale_y_continuous(limits = c(0,1), name = "mean detection accuracy [bars = SEM]") +
  scale_x_discrete(name = "Target Position") + 
  guides(fill = FALSE, color = FALSE) + 
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggsave(file.path(res_path,'figures','fig4_rt_acc.png'),width=w,height=h)
dev.copy(pdf,file.path(res_path,'figures','exp3fig4acc.pdf'), width = w, height = h)
dev.off()

```

### b. Accuracy per word
```{r}
# there's an unequal number of observations in each cell for the following reasons: 
  # 1. blocks were made to have one target from each position, but not for those targets to be equally distributed across words, so some blocks, e.g. subject 39, meta block 8, tgt word 4 has 35 observations because two of the targets in that block came from the same word. we didn't think to control for this, but i also can't see why it would be critical. 
  # 2. not all blocks x tgt words have the full n of obs (18, 36, 54) probably because observations were removed during the RT outlier removal phase. 

accuracy_data4 <- rt_data %>% 
  summarySE(measurevar = "detect", groupvars = c("tgt_word"),na.rm=TRUE)


accuracy_data4$tgt_word <- c("nugadi","rokise","mipola","zabetu")
stargazer(accuracy_data4, 
          type = "html", 
          out = file.path(res_path,'tables','word_accuracy.doc'), summary = FALSE, rownames = FALSE)

accuracy_data5 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_word","subject"),na.rm=TRUE)

# ------------ Averaged Data
word.lm <- lm(detect_mean ~ tgt_word, accuracy_data5)
summary(word.lm)
Anova(word.lm)
(em.word <- emmeans(word.lm, specs = pairwise ~ tgt_word, adjust = "tukey", transform = "response"))


```


```{r}
ggplot(accuracy_data5, aes(x = tgt_word, y = detect_mean, fill = tgt_word)) +
  geom_point(position = position_jitter(width = .07)) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 1, trim = FALSE) + 
  geom_point(accuracy_data4, mapping = aes(tgt_word, detect_mean), position = position_nudge(x = 0.2, y = 0)) +
  geom_errorbar(accuracy_data4, mapping=aes(tgt_word, y=detect_mean, ymin=detect_mean-se,
                                            ymax=detect_mean+se),
                position = position_nudge(x = 0.2, y = 0), width = 0.05, size = 1) +
  scale_fill_manual(values=wes_palette("Zissou1")[c(1,3,4,5)]) +
  scale_y_continuous(limits = c(0,1), name = "mean detection accuracy [bars = SEM]") +
  scale_x_discrete(name = "Pseudoword", labels = c("nugadi","rokise","mipola","zabetu")) + 
  guides(fill = FALSE, color = FALSE) + 
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggsave('fig4b_rt_acc.png',width=w,height=h)
dev.copy(pdf,file.path(res_path,'figures','exp3fig4bacc.pdf'), width = w, height = h)
dev.off()


# ggplot(tgt_acc_word_sum1, mapping=aes(y=accuracy_mean, x=tgt_word)) + 
#   geom_point(aes(color=subject)) + 
#   geom_boxplot(aes(group=as.factor(tgt_word)), alpha = .3, width = .3) + 
#   xlab("Target Word") + 
#   ylab("Mean detection accuracy") + 
#   theme_minimal() +
#   theme(text = element_text(family = "LM Roman 10", face="bold"), legend.position="none") +
#   ggtitle("B.") +
#   ggsave(file.path(res_path,'/figures/', '/targetdetection_accuracy_word.png'), width = w, height = h)

```
### c Accuracy per Syllable
```{r}
accuracy_data6 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("target","subject", "tgt_pos"),na.rm=TRUE) %>%
  mutate(target = factor(target, levels = c("nu","ga","di","ro","ki","se","mi","po","la","za","be","tu")))

accuracy_data7 <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("target"),na.rm=TRUE) %>%
  mutate(target = factor(target, levels = c("nu","ga","di","ro","ki","se","mi","po","la","za","be","tu")))

stargazer(accuracy_data7, 
          type = "html", 
          out = file.path(res_path,'tables','syllable_accuracy.doc'), summary = FALSE, rownames = FALSE)

# ------------ Averaged Data
syll.lm <- lm(detect_mean ~ target, accuracy_data6)
summary(syll.lm)
Anova(syll.lm)
(syll.em <- emmeans(syll.lm, specs = pairwise ~ target, adjust = "tukey", transform = "response"))


```


```{r}
ggplot(accuracy_data6, aes(x = target, y = detect_mean)) +
  geom_point(position = position_jitter(width = .07), aes(color = tgt_pos)) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 1, trim = FALSE,
                   fill = "gray") + 
  geom_point(accuracy_data7, mapping = aes(target, detect_mean), position = position_nudge(x = 0.2, y = 0)) +
  geom_errorbar(accuracy_data7, mapping=aes(target, y=detect_mean, ymin=detect_mean-se,
                                            ymax=detect_mean+se),
                position = position_nudge(x = 0.2, y = 0), width = 0.05, size = 1) +
  scale_color_brewer(palette="Dark2") + 
  scale_y_continuous(limits = c(0,1), name = "mean detection accuracy [bars = SEM]") +
  scale_x_discrete(name = "Target Syllables") + 
  guides(fill = FALSE) + labs(color = "Ordinal Position") +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) +
  ggsave('fig4c_rt_acc.png',width=9,height=6)
dev.copy(pdf,file.path(res_path,'/figures/','exp3fig4cacc.pdf'),width=9,height=6)
dev.off()

```


## Prove it didn't change bc of OR
Check: some accuracy test... -.-
```{r}
rt_data_cleaned.2 %>%
  summarise(mean = mean(detect),
            sd = sd(detect))

after <- rt_data %>% summarySE(measurevar = "detect", groupvars = c("subject"),na.rm=TRUE) 
before <- rt_data_cleaned.2 %>% summarySE(measurevar = "detect", groupvars = c("subject"),na.rm=TRUE) 

t.test(after$detect_mean, before$detect_mean, alternative = "two.sided")

rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos"),na.rm=TRUE) 
rt_data_cleaned.2 %>% summarySE(measurevar = "detect", groupvars = c("tgt_pos"),na.rm=TRUE) 

rt_data %>% summarySE(measurevar = "detect", groupvars = c("tgt_word"),na.rm=TRUE) 
rt_data_cleaned.2 %>% summarySE(measurevar = "detect", groupvars = c("tgt_word"),na.rm=TRUE) 

#rt_data %>% summarySE(measurevar = "detect", groupvars = c("target"),na.rm=TRUE) 

```


# --- Word Recognition
### Summarize Data
```{r}
# wordrec_data_sum1 <- wordrec_data %>%
#   group_by(subject) %>%
#   summarySE(measurevar = "prop_word_chosen",na.rm=TRUE)

wordrec_data_sum1 <- wordrec_data_orig %>%
  group_by(subject) %>%
  summarySE(measurevar = "prop_word_chosen",na.rm=TRUE)

```

### Fig. 5. Plot Data
```{r}
ggplot(wordrec_data_orig, aes(1,prop_word_chosen)) +
  # subjects
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = .5) +
  # mean/sd
  geom_point(data = wordrec_data_sum1, 
            mapping = aes(x = 1, y = prop_word_chosen_mean), position = position_nudge(.2), 
            colour = "BLACK", size = 1) +
  geom_errorbar(data = wordrec_data_sum1, 
            mapping = aes(x = 1, y = prop_word_chosen_mean, ymin = prop_word_chosen_mean-se, 
            ymax = prop_word_chosen_mean+se), position = position_nudge(.2), 
            colour = "BLACK", width = 0.07, size = 1) +
  # baseline
  geom_hline(aes(yintercept = 0.5), colour = "red", linetype = "dashed",show.legend = FALSE) +
  # axes
  scale_x_discrete(name='',breaks=waiver(),limits=c(0,1)) + # scale x 
  scale_y_continuous(name='P(word chosen over partword)',limits=c(0,1)) + # scale y
  # theme
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) + 
  theme(legend.position="none") + 
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank(),legend.position="none") +
  ggsave('exp3_fig5_wordrec.png', width = w, height = h)
dev.copy(pdf,file.path(res_path,'/figures/','exp3fig5_wr.pdf'), width = w, height = h)
dev.off()
```

#### T-Tests
```{r}
# Visualize Data
hist(wordrec_data$prop_word_chosen)
shapiro.test(wordrec_data$prop_word_chosen) # Non-significant difference = normality. Yep, normal.

# ttest
wordrec_ttest <- t.test(wordrec_data_orig$prop_word_chosen, mu = .5,alternative = "greater")
sd(wordrec_data_orig$prop_word_chosen)

# cohen's d - effect size 
wr_d <- cohensD(wordrec_data_orig$prop_word_chosen,mu = .5)
```

#### Post-hoc power analysis
```{r}
# power = 1-beta (type II error -- false reject)
# at p = 0.05
wr_p_05 <- pwr.t.test(d = wr_d, n = length(wordrec_data_orig$subject), sig.level = 0.05, power = NULL,
           alternative = "greater",type = "one.sample")
# at p = .01
wr_p_01 <- pwr.t.test(d = wr_d, n = length(wordrec_data_orig$subject), sig.level = 0.01, power = NULL,
                      alternative = "greater",type = "one.sample")

wr_p_50 <- pwr.t.test(d = wr_d, n = 60, sig.level = 0.05, power = NULL,
           alternative = "greater",type = "one.sample")
wr_p_15 <- pwr.t.test(d = wr_d, n = 15, sig.level = 0.05, power = NULL,
           alternative = "greater",type = "one.sample")
```
The mean word discrimination was significant (M = 0.62, SD = 0.19; t(29) = 3.38, p = 0.001, CI = 0.56; Cohen's d = 0.62) compared to a baseline mean of 0.5. 

We performed a post-hoc power analysis to further investigate the strength of the effect. At a significance level of 0.05, with a d of 0.62, and N of 30, power was 0.95. The same analysis at a stricter significance level of 0.01 yielded a power of 0.81. An analysis with alpha = 0.05, the same Cohen's d, and double the number of participants (N = 60), power is projected to be 0.99. With one-half the participants, (N = 15), power falls to 0.73. 


### Fig. 5b. Wordrec by Word
```{r}
wordrec_data_wrd <- wordrec_data_orig %>%
  gather(key = "word",value = "n_chosen", mipola,nugadi,rokise,zabetu) %>%
  mutate(word = fct_relevel(word,"nugadi","rokise","mipola","zabetu"))

  
wordrec_data_sum2 <- wordrec_data_wrd %>%
  summarySE(measurevar = "n_chosen", groupvars = "word",na.rm=TRUE) %>%
  mutate(word = fct_relevel(word,"nugadi","rokise","mipola","zabetu"))


ggplot(wordrec_data_wrd, mapping = aes(x=word,y=n_chosen, fill = word)) +
  geom_point(position = position_jitter(width = .07)) +
  geom_flat_violin(position = position_nudge(x = 0.2, y = 0), adjust = 1.2, trim = FALSE) + 
  geom_point(wordrec_data_sum2, mapping = aes(x=word, y=n_chosen_mean),
              position = position_nudge(x = 0.2, y = 0)) +
  geom_errorbar(wordrec_data_sum2, mapping = aes(x=word,y=n_chosen_mean,ymin = n_chosen_mean-se, 
                                       ymax = n_chosen_mean+se, group = 1),
                                position = position_nudge(x = 0.2, y = 0), width = 0.05, size = 1) +
  
  geom_hline(aes(yintercept = 2), colour = "red", linetype = "dashed",show.legend = FALSE) +

  # axes
  scale_x_discrete(name="Pseudoword", labels = ) +
  scale_y_continuous(name="N(word chosen over partword)",limits=c(0,4.5)) + 
  # theme
  scale_fill_manual(values=wes_palette("Zissou1")[c(1,3,4,5)]) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) + 
  theme(legend.position="none") +
  ggsave('exp3_fig5b_wr_word.png', width = w, height = h)
dev.copy(pdf,file.path(res_path,'/figures/','exp3fig5b_wr.pdf'), width = w, height = h)
dev.off()
```

```{r}
wordrec_data_sum2

p.s <- c(t.test(wordrec_data_orig$mipola, mu = 2)$p.value,
t.test(wordrec_data_orig$nugadi, mu = 2)$p.value,
t.test(wordrec_data_orig$rokise, mu = 2)$p.value,
t.test(wordrec_data_orig$zabetu, mu = 2)$p.value) 
p.s.B <- p.adjust(p.s,method = "bonferroni")

```


###### Analysis 
```{r}
wordrec_data_tbl <- data.frame(word=character(),
                 mean = double(),
                 sd = double(),
                 ci_lo = double(),
                 ci_hi = double(),
                 t = double(),
                 df = double(), 
                 p_val = double(),
                 stringsAsFactors=FALSE) 


## analysis: t-test of each set of responses (to each word) against baseline mean of 2. 
word_list <- (unique(wordrec_data_wrd$word))
for (curr_word in word_list) {
  curr_word_data <- wordrec_data_wrd %>%
                    filter(word == curr_word)
  curr_t <- t.test(curr_word_data$n_chosen, mu = 2)
  wordrec_data_tbl[nrow(wordrec_data_tbl)+1,] <- c(curr_word, 
                                                   curr_t$estimate, 
                                                   sd(curr_word_data$prop_word_chosen),  
                                                   curr_t$conf.int[1], 
                                                   curr_t$conf.int[2],
                                                   curr_t$statistic, 
                                                   curr_t$parameter,
                                                   curr_t$p.value)
  }
wordrec_data_tbl[,2:ncol(wordrec_data_tbl)] <- sapply(wordrec_data_tbl[,2:ncol(wordrec_data_tbl)], as.numeric)
print(wordrec_data_tbl, digits = 2)

wrd.table <- as.data.frame(wordrec_data_tbl)
wrd.table <- wrd.table %>% 
  mutate_if(is.numeric, round, digits = 3)
   wrd.table %>%
    kable() %>%
     kable_styling(bootstrap_options = c("striped", "hover")) %>%
     save_kable(file = 'wordrec_individ.png', self_contained = T) #width = w, height = h)



```
On average, participants were able to discriminate 3 out of 4 words from partwords above chance level (2/4).


# ----------------  Corrlations


## Corr Median Delta with Wordrec
```{r}
# Generate Deltas for Experiment 3 Data... Delta MEDIANS
rt_data_sum_corr <- rt_data %>% 
    group_by(subject) %>%
    mutate(rt_sc.s = scale(rt)) %>% # scale for each subject
    summarySE(measurevar="rt_sc.s", groupvars=c("subject","tgt_pos"), na.rm=TRUE)

options(scipen=999)

exp_3_data_delta <- rt_data_sum_corr %>% 
  arrange(subject) %>%
  group_by(subject) %>%
  mutate(delta = rt_sc.s_median - lead(rt_sc.s_median,default=first(rt_sc.s_median))) %>%
  #mutate(delta = rt_median - lead(rt_median,default=first(rt_median))) %>%
  mutate(delta = round(delta,digits=5))

#This works for 1-2 and 2-3, but for 3-1 it pulls the "1" not from the same group, but from the next item in the array.
# Add a column where each rt_median is subtracted by value in n+2, and then shift tha column down so this "1-3" item sits at the tgt_pos 3 row...
exp_3_data_delta <- exp_3_data_delta %>%
    arrange(subject) %>%
    group_by(subject) %>%
    mutate(delta1.3 = rt_sc.s_median - lead(rt_sc.s_median,n=2)) %>%
    mutate(delta1.3 = data.table::shift(delta1.3,n=2))
# take those values in tgt_pos 3 rows...
vals.1.3 <- exp_3_data_delta$delta1.3[which(exp_3_data_delta$tgt_pos==3)]
# add them to the delta col... 
exp_3_data_delta$delta[which(exp_3_data_delta$tgt_pos==3)] <- vals.1.3
# and remove the temp col
exp_3_data_delta <- exp_3_data_delta %>% dplyr::select(-delta1.3)

exp_3_data_delta <- exp_3_data_delta %>%
  dplyr::select(subject:N,delta,rt_sc.s_mean:ci) %>%
  #select(subject:N,delta,rt_mean:ci) %>%
  dplyr::rename(., delta_rt = tgt_pos) %>%
  mutate(
    delta_rt = case_when(delta_rt==1 ~ "D1-2",
                         delta_rt==2 ~ "D2-3",
                         delta_rt==3 ~ "D1-3"))
exp_3_data_delta$delta_rt <- factor(exp_3_data_delta$delta_rt, levels = c("D1-2", "D2-3", "D1-3"))
```

Select only word recognition data from participants in the set: 
```{r}
wordrec_data_corr <- wordrec_data_orig[(wordrec_data_orig$subject) %in% unique(exp_3_data_delta$subject),] 
exp_3_data_delta <- exp_3_data_delta[(exp_3_data_delta$subject) %in% unique(wordrec_data_corr$subject),] 
length(unique(wordrec_data_corr$subject))
```

Correlate
```{r warning=FALSE}
corr1.2 <- merge(exp_3_data_delta %>% filter(delta_rt == "D1-2") %>%  dplyr::select(delta), wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))

corr2.3 <- merge(exp_3_data_delta %>% filter(delta_rt == "D2-3") %>%  dplyr::select(delta),wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))

corr1.3 <- merge(exp_3_data_delta %>% filter(delta_rt == "D1-3") %>%  dplyr::select(delta),wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))
```

```{r}
corrtest.1.2 <- cor.test(corr1.2$delta,corr1.2$prop_word_chosen, method = "pearson")
corrtest.2.3 <- cor.test(corr2.3$delta,corr2.3$prop_word_chosen, method = "pearson")
corrtest.1.3 <- cor.test(corr1.3$delta,corr1.3$prop_word_chosen, method = "pearson")

```

### Fig. 6. Delta Medians v. Wordrec
```{r}
plot.corr <- data.frame(subject = corr1.2$subject, 
                        delta1.2 = corr1.2$delta,
                        delta2.3 = corr2.3$delta,
                        delta1.3 = corr1.3$delta,
                        prop.word = corr1.2$prop_word_chosen) %>%
            gather(key = "d.pos", value = "d.med", delta1.2, delta2.3, delta1.3) %>%
            mutate(d.pos = factor(d.pos, levels = c("delta1.2", "delta2.3","delta1.3")))


ggplot(data = plot.corr, aes(d.med, prop.word, color = d.pos)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_smooth(method = lm, se = FALSE, size = 1.1) +
  scale_color_manual(values = c("#D44739", "#FAC869", "#3C5E4D"),
                     name = NULL, labels = c("1st - 2nd", "2nd - 3rd", "1st - 3rd")) +
  xlab("proportional change in median RT") + ylab("P(word chosen over partword)") +
annotate(geom = "text", x = 1.5, y = 0.5, label = paste0("\u03C1 = ",round(corrtest.1.2$estimate, digits = 2),", p = ",round(corrtest.1.2$p.value, digits = 2)), color = "#D44739") + 
annotate(geom = "text", x = 1.5, y = 0.45, label = paste0("\u03C1 = ",round(corrtest.2.3$estimate, digits = 2),", p = ",round(corrtest.2.3$p.value, digits = 2)), color = "#FAC869") +   
annotate(geom = "text", x = 1.49, y = 0.4, label = paste0("\u03C1 = ",round(corrtest.1.3$estimate, digits = 2),", p = ",round(corrtest.1.3$p.value, digits = 2)), color = "#3C5E4D") +   
  geom_vline(xintercept = 0, color = "gray", linetype="dashed") + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), 
        legend.title = element_text(""),  legend.position = "top") +
  ggsave('fig6_corr_sc.png', width = w, height = h)  
```


## Corr Mean Delta with Wordrec

```{r}
# Generate Deltas for Experiment 3 Data... Delta MEDIANS
rt_data_sum_corr <- rt_data %>% 
    group_by(subject) %>%
    mutate(rt_sc.s = scale(rt)) %>% # scale for each subject
    summarySE(measurevar="rt_sc.s", groupvars=c("subject","tgt_pos"), na.rm=TRUE)

options(scipen=999)

exp_3_data_delta.mu <- rt_data_sum_corr %>% 
  arrange(subject) %>%
  group_by(subject) %>%
  mutate(delta = rt_sc.s_mean - lead(rt_sc.s_mean,default=first(rt_sc.s_mean))) %>%
  mutate(delta = round(delta,digits=5))

#This works for 1-2 and 2-3, but for 3-1 it pulls the "1" not from the same group, but from the next item in the array.
# Add a column where each rt_median is subtracted by value in n+2, and then shift tha column down so this "1-3" item sits at the tgt_pos 3 row...
exp_3_data_delta.mu <- exp_3_data_delta.mu %>%
    arrange(subject) %>%
    group_by(subject) %>%
    mutate(delta1.3 = rt_sc.s_mean - lead(rt_sc.s_mean,n=2)) %>%
    mutate(delta1.3 = data.table::shift(delta1.3,n=2))
# take those values in tgt_pos 3 rows...
vals.1.3 <- exp_3_data_delta.mu$delta1.3[which(exp_3_data_delta.mu$tgt_pos==3)]
# add them to the delta col... 
exp_3_data_delta.mu$delta[which(exp_3_data_delta.mu$tgt_pos==3)] <- vals.1.3
# and remove the temp col
exp_3_data_delta.mu <- exp_3_data_delta.mu %>% dplyr::select(-delta1.3)

exp_3_data_delta.mu <- exp_3_data_delta.mu %>%
  dplyr::select(subject:N,delta,rt_sc.s_mean:ci) %>%
  #select(subject:N,delta,rt_mean:ci) %>%
  dplyr::rename(., delta_rt = tgt_pos) %>%
  mutate(
    delta_rt = case_when(delta_rt==1 ~ "D1-2",
                         delta_rt==2 ~ "D2-3",
                         delta_rt==3 ~ "D1-3"))
exp_3_data_delta.mu$delta_rt <- factor(exp_3_data_delta.mu$delta_rt, levels = c("D1-2", "D2-3", "D1-3"))
```
Select only word recognition data from participants in the set: 
```{r}
wordrec_data_corr <- wordrec_data_orig[(wordrec_data_orig$subject) %in% unique(exp_3_data_delta.mu$subject),] 
exp_3_data_delta.mu <- exp_3_data_delta.mu[(exp_3_data_delta.mu$subject) %in% unique(wordrec_data_corr$subject),] 
```

Correlate
```{r warning=FALSE}
corr1.2.mu <- merge(exp_3_data_delta.mu %>% filter(delta_rt == "D1-2") %>%  dplyr::select(delta), wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))

corr2.3.mu <- merge(exp_3_data_delta.mu %>% filter(delta_rt == "D2-3") %>%  dplyr::select(delta),wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))

corr1.3.mu <- merge(exp_3_data_delta.mu %>% filter(delta_rt == "D1-3") %>%  dplyr::select(delta),wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))
```

```{r}
corrtest.1.2.mu <- cor.test(corr1.2.mu$delta,corr1.2.mu$prop_word_chosen, method = "pearson")
corrtest.2.3.mu <- cor.test(corr2.3.mu$delta,corr2.3.mu$prop_word_chosen, method = "pearson")
corrtest.1.3.mu <- cor.test(corr1.3.mu$delta,corr1.3.mu$prop_word_chosen, method = "pearson")

```

### Fig. 6. Delta Means v. Wordrec
```{r}
plot.corr.mu <- data.frame(subject = corr1.2.mu$subject, 
                        delta1.2 = corr1.2.mu$delta,
                        delta2.3 = corr2.3.mu$delta,
                        delta1.3 = corr1.3.mu$delta,
                        prop.word = corr1.2.mu$prop_word_chosen) %>%
            gather(key = "d.pos", value = "d.mu", delta1.2, delta2.3, delta1.3) %>%
            mutate(d.pos = factor(d.pos, levels = c("delta1.2", "delta2.3","delta1.3")))


ggplot(data = plot.corr.mu, aes(d.mu, prop.word, color = d.pos)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_smooth(method = lm, se = FALSE, size = 1.1) +
  scale_color_manual(values = c("#D44739", "#FAC869", "#3C5E4D"),
                     name = NULL, labels = c("1st - 2nd", "2nd - 3rd", "1st - 3rd")) +
  xlab("proportional change in mean RT") + ylab("P(word chosen over partword)") +
annotate(geom = "text", x = 1.25, y = 0.5, label = paste0("\u03C1 = ",round(corrtest.1.2.mu$estimate, digits = 2),", p = ",round(corrtest.1.2.mu$p.value, digits = 2)), color = "#D44739") + 
annotate(geom = "text", x = 1.25, y = 0.45, label = paste0("\u03C1 = ",round(corrtest.2.3.mu$estimate, digits = 2),", p = ",round(corrtest.2.3.mu$p.value, digits = 2)), color = "#FAC869") +   
annotate(geom = "text", x = 1.25, y = 0.4, label = paste0("\u03C1 = ",round(corrtest.1.3.mu$estimate, digits = 2),", p = ",round(corrtest.1.3.mu$p.value, digits = 2)), color = "#3C5E4D") +   
  geom_vline(xintercept = 0, color = "gray", linetype="dashed") + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), 
        legend.title = element_text(""),  legend.position = "top") +
  ggsave('fig6_corr_sc_mu.png', width = w, height = h)  
```


## Batterink 2017
From Batterink & Paller 2017:
"Finally, an RT score was computed for each individual participant by subtracting the corrected median RT to third syllable targets from the corrected median RT to first syllable targets, with larger values indicating greater facilitation."

"Mean RT score across participant (computed as the RT difference between first syllable targets and third syllable targets) was 79.1 msec (SD = 59.7), significantly above chance [t(23)  6.49, p < .001]."

"Performance on the rating task and target detection task significantly correlated across participants (rating score: r = .51, p = .010; rating accuracy: r = .42, p = .044), indicating that learners who performed better on the rating task also showed larger facilitation effects on the target detection task. Given that the rating task provides a measure of explicit memory, this correlation suggests that the target detection task is at least somewhat sensitive to explicit memory as well. Nonetheless, a subgroup of participants (n = 7) who did not achieve above 50% accuracy on the rating task (mean = 45%, SD = 4.4%) still showed a significant RT effect [Corrected RTs: Syllable Position effect: F(2,12) = 6.11, p = .030; linear effect of Syllable Position: F(1,6) = 28.7, p = .002]."




From Batterink et al. 2015:
Exp 1: "Correlations were calculated between each participants recognition score and their RT priming effect, computed as the RT difference between initial position and final position syllables (RT1RT3). As shown in Fig. 1B, there was no significant correlation between these two measures (r = .07, p = .75, 95% CI for r = -.34 to .46)."

Exp 2: "As in Experiment 1, the across-subject correlation between recognition scores and the magnitude of the RT priming effect (RT1RT3) on the target detection task was nonsignif- icant (r = .26, p = .20, 95% CI for r = -.15 to .60). However, this correlation may have been artificially inflated by three participants who showed no behavioral evidence of learning as assessed by either the recognition or the RT measure [criteria: <50% accuracy in recognition task, <10 ms effect (RT1RT3) in target detection task]. When these three par- ticipants were excluded from the sample, there was still no trend for a correlation between recognition and RT (r=.17, p = .45, 95% CI for r = -.27 to .55)."

Even including "all participants from both experiments, with the exception of the 3 nonlearners identified in Experiment 2 (n = 46). No significant correlation was found between recognition and RT priming (r = .11, p = .47, 95% CI for r = -.19 to .39)."

```{r}
# calculate
rt_data_sum_corr.2 <- rt_data %>% 
    summarySE(measurevar="rt", groupvars=c("subject","tgt_pos"), na.rm=TRUE)

exp_3_data_delta.batterink2017 <- rt_data_sum_corr.2 %>% 
  group_by(subject) %>%
  mutate(delta = rt_median - lead(rt_median, n=2)) %>%
  mutate(delta = round(delta,digits=5)) %>%
  dplyr::select(subject:rt_median,delta,sd:ci) %>%
  filter(tgt_pos == 1)

# summary
mean(exp_3_data_delta.batterink2017$delta)
sd(exp_3_data_delta.batterink2017$delta)

t.test(exp_3_data_delta.batterink2017$delta, mu = 0, alternative = "greater")

# subset
wordrec_data_corr <- wordrec_data_orig[(wordrec_data_orig$subject) %in% unique(exp_3_data_delta.batterink2017$subject),] 
exp_3_data_delta.batterink2017 <- exp_3_data_delta.batterink2017[(exp_3_data_delta.batterink2017$subject) %in% unique(wordrec_data_corr$subject),] 

# merge
corr.batterink2017 <- merge(exp_3_data_delta.batterink2017,
                      wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))
# correlate
corrtest.batterink2017 <- cor.test(corr.batterink2017$delta,
                                   corr.batterink2017$prop_word_chosen, 
                                   method = "pearson")

```

### Fig. a.
```{r}

ggplot(data = corr.batterink2017, aes(delta, prop_word_chosen)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_smooth(method = lm, se = FALSE, size = 1.1) +
  scale_color_manual(values = c("#D44739", "#FAC869", "#3C5E4D"),
                     name = NULL, labels = c("1st - 2nd", "2nd - 3rd", "1st - 3rd")) +
  xlab("RT score (as per Batterink 2017)") + ylab("P(word chosen over partword)") +
annotate(geom = "text", x = 275, y = 0.2, 
         label = paste0("\u03C1 = ", round(corrtest.batterink2017$estimate, digits = 2),", p = ",round(corrtest.batterink2017$p.value, digits = 2)), color = "#D44739") +   
  geom_vline(xintercept = 0, color = "gray", linetype="dashed") + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), 
        legend.title = element_text(""),  legend.position = "top") +
   ggsave(file.path(res_path,'figures','batterink_corr.png'), width = w, height = h)
  
```


## Siegelman et al. 2018

Online Measure of SL = log.RT() 1st position) - mean.log.RT(2nd & 3rd position)

```{r}

# calculate
rt_data_sum_corr.3a <- rt_data %>% 
    mutate(rt_log = log(rt)) %>%
    summarySE(measurevar="rt_log", groupvars=c("subject","tgt_pos"), na.rm=TRUE) %>%
    filter(tgt_pos == 1)


rt_data_sum_corr.3b <- rt_data %>% 
    mutate(rt_log = log(rt)) %>%
    group_by(subject) %>%
    filter(tgt_pos == 2 || 3) %>%
    summarySE(measurevar="rt_log", groupvars=c("subject"), na.rm=TRUE) %>%
    add_column(tgt_pos = as.factor("2-3"), .after = "subject")

rt_data_sum.corr.3 <- rbind(rt_data_sum_corr.3a,rt_data_sum_corr.3b) %>%
  arrange(subject)


exp_3_data_delta.siegelman2018 <- rt_data_sum.corr.3 %>% 
  group_by(subject) %>%
  mutate(delta = rt_log_mean - lead(rt_log_mean)) %>%
  mutate(delta = round(delta,digits=5)) %>%
  dplyr::select(subject:rt_log_median,delta,sd:ci) %>%
  filter(tgt_pos == 1)

# summary
mean(exp_3_data_delta.siegelman2018$delta)
sd(exp_3_data_delta.siegelman2018$delta)

# subset
wordrec_data_corr <- wordrec_data_orig[(wordrec_data_orig$subject) %in% unique(exp_3_data_delta.batterink2017$subject),] 
exp_3_data_delta.siegelman2018 <- exp_3_data_delta.siegelman2018[(exp_3_data_delta.siegelman2018$subject) %in% unique(wordrec_data_corr$subject),] 

# merge
corr.siegelman2018 <- merge(exp_3_data_delta.siegelman2018,
                      wordrec_data_corr %>% dplyr::select(subject, prop_word_chosen))
# correlate
corrtest.siegelman2018 <- cor.test(corr.siegelman2018$delta,
                                   corr.siegelman2018$prop_word_chosen, 
                                   method = "pearson",
                                     
                                  )

```

###
```{r}
ggplot(data = corr.siegelman2018, aes(delta, prop_word_chosen)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_smooth(method = lm, se = FALSE, size = 1.1) +
  scale_color_manual(values = c("#D44739", "#FAC869", "#3C5E4D"),
                     name = NULL, labels = c("1st - 2nd", "2nd - 3rd", "1st - 3rd")) +
  xlab("RT score (as per Siegelman 2018)") + ylab("P(word chosen over partword)") +
annotate(geom = "text", x = 0.45, y = 0.2, 
         label = paste0("\u03C1 = ", round(corrtest.siegelman2018$estimate, digits = 2),", p = ",round(corrtest.siegelman2018$p.value, digits = 2)), color = "#D44739") +   
  geom_vline(xintercept = 0, color = "gray", linetype="dashed") + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), 
        legend.title = element_text(""),  legend.position = "top") +
  ggsave(file.path(res_path,'figures','siegelman_corr.png'), width = w, height = h)
```

#----------------------------
## Siegelman Analyses
```{r}
rt_data <- rt_data %>% mutate(rt_log = log(rt))

rt_data_log_sum <- rt_data %>%
  summarySE(measurevar="rt_log", groupvars=c("tgt_pos","block"), na.rm=TRUE)

ggplot(data = rt_data_log_sum, aes(x = block, y = rt_log_mean, group = tgt_pos, color = tgt_pos)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_line(size = 1.5, alpha = 0.5) + 
  geom_smooth(method = "glm", formula = y~x,
              method.args = list(family = gaussian(link = 'log')), 
              se = TRUE, size = 1, alpha = 0.2) +
  scale_color_manual(values = c("#D44739", "#FAC869", "#3C5E4D"),
                     name = NULL, labels = c("1st", "2nd", "3rd")) +
  xlab("Block") + ylab("Mean log(RT)") +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), 
        legend.title = element_text("Position"),  legend.position = "right") + 
  ggsave(file.path(res_path,'figures','logRT_block.png'), width = w, height = h)
# dev.copy(pdf,file.path(res_path,'figures','fig1artposblock.pdf'), width = 6, height = 4)
# dev.off()

```


```{r}

exp_3_log_traj <- rbind(rt_data_log_sum %>% filter(tgt_pos == 1),
    rt_data %>%
    filter(tgt_pos == 2 || 3) %>%
    summarySE(measurevar="rt_log", groupvars=c("block"), na.rm=TRUE) %>%
    add_column(tgt_pos = as.factor("2-3"), .before = "block"))

exp_3_log_traj.siegelman2018 <- exp_3_log_traj %>% 
  arrange(block) %>%
  mutate(delta = rt_log_mean - lead(rt_log_mean)) %>%
  mutate(delta = round(delta,digits=5)) %>%
  dplyr::select(tgt_pos:rt_log_median,delta,sd:ci) %>%
  filter(tgt_pos == 1)


ggplot(data = exp_3_log_traj.siegelman2018, aes(x = block, y = rt_log_mean, group = 1)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_line(size = 1.5, alpha = 0.5) +
  geom_errorbar(mapping = aes(ymin = rt_log_mean-se, ymax = rt_log_mean+se), colour = "BLACK", width = 0.1, size = 0.8) + 
  geom_smooth(method = "glm", formula = y~x,
              method.args = list(family = gaussian(link = 'log')), 
              se = TRUE, size = 1, alpha = 0.2) +
  xlab("Block") + 
  ylab("Measure of Online SL") +
  #ylab(expression(logRT[1]~-~mu(logRT[2]+logRT[3]))) + 
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10", face="bold"), 
        legend.title = element_text("Position"),  legend.position = "right") + 
  ggsave(file.path(res_path,'figures','logRT_block_traj.png'), width = w, height = h)


```



```{r}


exp_3_log_traj_ind <- rbind(rt_data %>% 
  summarySE(measurevar="rt_log", groupvars=c("subject","tgt_pos","block"), na.rm=TRUE) %>%
  filter(tgt_pos == 1),
 rt_data %>%
    filter(tgt_pos == 2 || 3) %>%
    summarySE(measurevar="rt_log", groupvars=c("subject","block"), na.rm=TRUE) %>%
    add_column(tgt_pos = as.factor("2-3"), .before = "block")) %>%
  arrange(block,subject)

exp_3_log_traj_ind.siegelman2018 <- exp_3_log_traj_ind %>% 
  mutate(delta = rt_log_mean - lead(rt_log_mean)) %>%
  mutate(delta = round(delta,digits=5)) %>%
  dplyr::select(subject:rt_log_median,delta,sd:ci) %>%
  filter(tgt_pos == 1)

library(pbkrtest)
library(emmeans)
emm_options(lmer.df = "satterth")

traj.mod1 <- lmer(delta ~ 1 + block + (1|subject), data = exp_3_log_traj_ind.siegelman2018)
#, family = gaussian(link="log"))

summary(traj.mod1)
Anova(traj.mod1)
emmeans(traj.mod1, specs = pairwise ~ block, adjust = "Tukey",  transform = "response")

# http://www.alexanderdemos.org/ANOVA6.html

# cont <- emmeans(traj.mod1, ~ block) #we already created this
# pairs(cont, adjust='tukey')

descdist(exp_3_log_traj_ind.siegelman2018$rt_log_mean[!is.na(exp_3_log_traj_ind.siegelman2018$rt_log_mean)])
gofstat(fitdist(exp_3_log_traj_ind.siegelman2018$rt_log_mean[!is.na(exp_3_log_traj_ind.siegelman2018$rt_log_mean)],"lnorm"))
denscomp(fitdist(exp_3_log_traj_ind.siegelman2018$rt_log_mean[!is.na(exp_3_log_traj_ind.siegelman2018$rt_log_mean)],"lnorm"))
```

So, nothing new is gained in the above analysis. Using logRT, we find again that there's no effect of block on reaction times, again likely because the learning is happening in the first few presentations in each block.  

#----------------------------
 Corr. Delta / Wordrec per Word
```{r warning=FALSE}
# wrangle
rt_data_sum_corr2 <- rt_data %>% # subject x position x word
  summarySE(measurevar = "rt", groupvars = c("subjID","subject","tgt_pos","tgt_word"),na.rm=TRUE) 

rt_data_sum_corr3 <- rt_data %>%
  summarySE(measurevar = "rt", groupvars = c("subjID","subject","tgt_pos","tgt_word","block"),na.rm = TRUE)

# calculate delta_means for each participant: 
    # mean_pos3-mean_pos1 / mean_pos1
  delta_means2 <-  data.frame(subj_id=character(),
                            subject=numeric(),
                            word=numeric(),
                            delta_mean=numeric(),
                             stringsAsFactors=FALSE)

    for (subj in unique(rt_data_sum_corr2$subjID)) {
      subj_subset <- rt_data_sum_corr2[which(rt_data_sum_corr2$subjID == subj),]  
      for (wrd in unique(subj_subset$tgt_word)) {
        subj_subsubset <- subj_subset %>% filter(tgt_word == wrd)
        
        subj_delta <- (subj_subsubset$rt_mean[3]-subj_subsubset$rt_mean[1])/subj_subsubset$rt_mean[1]
        
        delta_means2[nrow(delta_means2) + 1,] = list(subj, subj_subset$subject[1], wrd, subj_delta)
      }
    }

# subject h0207 had no hits on 1st pos. tgts for word 2. try with NA and with 0. 
  # -- no outstanding notes for this subject, likely just missed it = "ro"

  # subject b0207 missing data for 1st pos. tgts for word 2. 
                        # and for 2nd pos. tgts for word 3. this should be NA.
  # -- this is the subj for whom we lost 1/2 the data set. 
delta_means2$delta_mean[is.nan(delta_means2$delta_mean)] <- 0

# ensure same subjects
wordrec_data_corr2 <- wordrec_data[wordrec_data$subj_id %in% unique(rt_data_sum_corr2$subjID),] # correct! 

# word 1 = nugadi
# word 2 = rokise
# word 3 = mipola
# word 4 = zabetu

wordrec_byword <- wordrec_data_corr2 %>%
  dplyr::select(subject, subj_id, nugadi, rokise, mipola, zabetu)
wordrec_byword[,3:6]<- wordrec_byword[,3:6]/4
wordrec_byword <- gather(wordrec_byword,key = tgt_word, value = prop_word_chosen, nugadi, rokise, mipola, zabetu)


wordrec_byword$tgt_word[wordrec_byword$tgt_word=="nugadi"] <- 1
  wordrec_byword$tgt_word[wordrec_byword$tgt_word=="rokise"] <- 2
    wordrec_byword$tgt_word[wordrec_byword$tgt_word=="mipola"] <- 3
      wordrec_byword$tgt_word[wordrec_byword$tgt_word=="zabetu"] <- 4

wordrec_byword <- wordrec_byword[order(wordrec_byword$tgt_word),]
wordrec_byword <- wordrec_byword[order(wordrec_byword$subject),]
delta_means2 <- delta_means2[order(delta_means2$word),]
delta_means2 <- delta_means2[order(delta_means2$subject),]


# correlate
corr_mat2 <- cbind(delta_means2,wordrec_byword) 
colnames(corr_mat2) <- c("subj_id", "subject", "word", "delta_mean", "subject2", "subj_id2", "tgt_word", "prop_word_chosen")
corr_mat2 <- corr_mat2 %>%
  dplyr::select(subj_id,tgt_word,delta_mean,prop_word_chosen)

corr_mat2 <- corr_mat2 %>%
  mutate(tgt_word = as.factor(tgt_word),
         subj_id = as.factor(subj_id))

SL_cortest2 <- cor.test(corr_mat2$delta_mean,corr_mat2$prop_word_chosen, method = "pearson")

# paired samples
SL_d2 <- cohensD(x = corr_mat2$delta_mean, y = corr_mat2$prop_word_chosen, method = "paired")
```

Fig. A. Plot
```{r warning=FALSE}
# Plot
ggscatter(corr_mat2, x = "delta_mean", y = "prop_word_chosen", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "% change RT (3rd Pos vs. 1st Pos)", ylab = "Prop. correct word recognition") + 
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) + 
  ggtitle('') +
  ggsave(file.path(res_path,'/figures/','/SL_corr-individ.png'), width = w, height = h)
```

Fig. B. Grouped across performance levels
```{r warning=FALSE}
ggplot() + 
  geom_point(corr_mat2, mapping = aes(x = prop_word_chosen, y = delta_mean, color = tgt_word),
             size = 1.5) + 
  geom_boxplot(corr_mat2, mapping = aes(x = prop_word_chosen, y = delta_mean, group = prop_word_chosen), alpha=0.4, width = .08) +
  scale_x_discrete(name="Prop. words correct (out of 4)", 
                    limits=c(0,.25,.5,.75,1)) +
  scale_y_continuous(name="% change RT (3rd Pos vs. 1st Pos)") +
  scale_color_manual(values = word_pal, labels = c("nugadi","rokise","mipola","zabetu")) +
  labs(color="Target Word") + 
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) + 
  ggtitle('') +
  ggsave(file.path(res_path,'/figures/','/corr_sl_individ.png'), width = w, height = h)
```
 Fig. C. Plot Individual delta means/word corrects
```{r warning=FALSE}

plot_corr <- corr_mat2 # %>%
            # filter(tgt_word==1)

word_names <- c(`1` = "nugadi",
                `2` = "rokise",
                `3` = "mipola",
                `4` = "zabetu")

w = 10
h = 7
ggplot(plot_corr,aes(x=prop_word_chosen,y=delta_mean,color=tgt_word)) +
  geom_jitter(size=2,width=.01) +
  geom_smooth(method=loess,se=FALSE,fullrange=TRUE) +
  scale_x_discrete(name="Prop. words correct (out of 4)", 
                    limits=c(0,.25,.5,.75,1)) +
  scale_y_continuous(name="% change RT (3rd Pos vs. 1st Pos)") +
  facet_grid(.~ tgt_word, labeller = as_labeller(word_names)) +
  scale_color_manual(values = word_pal, guide = FALSE) +
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) + 
  ggtitle('') +
  ggsave(file.path(res_path,'/figures/','/corr_sl_by_word.png'), width = w, height = h)




```

 GLM
```{r}
# factorize? 
corr_mat2 <- corr_mat2 %>%
  mutate(prop_word_chosen_fct = as.factor(prop_word_chosen))

shapiro.test(corr_mat2$delta_mean)
# delta means formally dist. 
# logistic regression: categorical variable y = 

model.1 <- glmer(prop_word_chosen ~ - 1 + delta_mean + (1 | subj_id) , data = corr_mat2, family = binomial)
summary(model.1)

model.2 <- glmer(prop_word_chosen_fct ~ - 1 + delta_mean*tgt_word + (1 | subj_id) , data = corr_mat2, family = binomial)
summary(model.2)

anova(model.1, model.2) # --> wow, model 2! 

allEffects(model.2)
plot(allEffects(model.2))

# model.1 <- glmer(delta_mean ~ - 1 + prop_word_chosen + (1 | subj_id) , data = corr_mat2, family = gaussian)
# summary(model.1)
# 
# model.2 <- glmer(delta_mean ~ - 1 + prop_word_chosen*tgt_word + (1 | subj_id) , data = corr_mat2, family = gaussian)
# summary(model.2)
# 
# anova(model.1, model.2) 

em_sl_corr <- emmeans(model.2, ~ tgt_word | delta_mean)

pairs(em_sl_corr, simple = "each")

slcorr_mc <- contrast((em_sl_corr), interaction = "pairwise") 
slcorr_mc_regrid <- contrast(regrid(em_sl_corr), interaction = "pairwise")

# save to kabel
 slcorr.table <- data.frame(Estimate = coef(summary(slcorr_mc)),
                             "Std Error" = summary(slcorr_mc)$test$sigma,
                             "t value" = summary(slcorr_mc)$test$tstat,
                             P = summary(slcorr_mc)$test$pvalues)
 
  #row.names(tgt.table) <- c("Tgt_Pos1","Tgt_Pos2","Tgt_Pos3")
  #tgt.table$P<- c("<.001","<.001","<.001")
  tgt.table %>%
    kable() %>%
     kable_styling(bootstrap_options = c("striped", "hover")) %>%
     save_kable(file = 'sl_corr_contrasts.png', self_contained = T) #width = w, height = h)


```



TD Accuracy vs. Wordrec 
```{r}

wrd_perf_df <- as.data.frame(wordrec_byword$prop_word_chosen)
acc_word_corr <- cbind(tgt_acc_word_sum1,wrd_perf_df)
names(acc_word_corr)[9] <- "prop_word_chosen"

ggscatter(acc_word_corr, x = "prop_word_chosen", y = "accuracy_mean", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prop. words correct", ylab = "Mean Detection Performance") + 
  theme_minimal() +
  theme(text = element_text(family = "LM Roman 10", face="bold")) + 
  ggsave(file.path(res_path,'/figures/','/tgtdetectaccuracy_prop_word.png'), width = w, height = h)

```


Filter Best-Learned Words 
```{r}
# # word 1 = nugadi
# # word 2 = rokise
# # word 3 = mipola
# # word 4 = zabetu
# 
# wordrec_data_learning <- wordrec_data[,c(2,6:9)]
# wordrec_data_learning[wordrec_data_learning<3] <- NA
# wordrec_data_learned <- cbind.data.frame(wordrec_data$subject, wordrec_data_learning) 
#   colnames(wordrec_data_learned)[1] <- "subject" 
#   wordrec_data_learned <- wordrec_data_learned %>%
#     group_by(subject) %>%
#     dplyr::summarise(n_learned = sum(!is.na(c(mipola,nugadi,rokise,zabetu))),
#                      # calulate proportion correct based only on the ones they learned
#                      prop_learned = sum(mipola,nugadi,rokise,zabetu,na.rm = TRUE)/(n_learned*4)) 
#   wordrec_data_learned <- cbind.data.frame(wordrec_data_learned[1],wordrec_data_learning,wordrec_data_learned[,2:3])
# 
# row_count = 1
# for (subj in wordrec_data_learned$subj_id) {
#   which_learned <- vector()
#   temp <- wordrec_data_learned %>%
#     filter(subj_id == subj) 
#     if (!is.na(temp$mipola)) {
#       which_learned <- cbind(which_learned,3) 
#     } 
#     if (!is.na(temp$nugadi)) {
#       which_learned <- cbind(which_learned,1) 
#     }
#     if (!is.na(temp$rokise)) {
#       which_learned <- cbind(which_learned,2)  
#     }
#     if (!is.na(temp$zabetu)) {
#       which_learned <- cbind(which_learned,4) }
#   temp$learned <- list(as.list(which_learned))
#   
#   if (row_count == 1) {
#     wordrec_data_learnt <- temp
#   } else {
#     wordrec_data_learnt <- rbind(wordrec_data_learnt,temp)
#   }
#   row_count = row_count + 1
# }
# # wordrec_data_learned <- wordrec_data %>%
# #   filter_at(vars(mipola,nugadi,rokise,zabetu), any_vars(. > 2)) 
# # 
# # # number of participants that learned at least one word above chance
# # N_learned_words <- length(unique(wordrec_data_learned$subject))

```

```{r}
# # For each subject, filter out their data based on the list of numbers in the $learned column, 
# # Remove subjects who have NULL in that column
# subjects_none_learned <- wordrec_data_learnt$subj_id[which(wordrec_data_learnt$n_learned==0)]
# # all the others
# wordrec_data_learnt2 <- wordrec_data_learnt[which(wordrec_data_learnt$n_learned>0),]
# 
#   # how to check to see if an empty list is empty... 
#   # length(unlist(wordrec_data_learnt$learned[19])) # because in a df, an empty list still gives a length of 1, but if you unlist the data, it will give a length of 0 
# 
# # filter rt_data based on participants who had at least 1 word above chance
# rt_data_learned <- rt_data
# for (subj in subjects_none_learned) {
#   rt_data_learned <- rt_data_learned[!(rt_data_learned$subjID==subj),] }
# 
# # filter the rest based on the words they learned
# row_count = 1
# for (subj in unique(rt_data_learned$subjID)) {
#   # find the words that this participant got right
#   words_to_keep <- wordrec_data_learnt2 %>%
#     filter(subj_id == subj) 
#   words_to_keep <- unlist(words_to_keep$learned)
#   # filter the rt_data by that word
#   temp <- rt_data_learned %>%
#     filter(subjID == subj) %>%
#     filter(tgt_word %in% words_to_keep)
#   # build new 
#   if (row_count == 1) {
#     rt_data_learnt <- temp
#   } else {
#     rt_data_learnt <- rbind(rt_data_learnt,temp)
#   }
#   row_count = row_count + 1
# }

```

Corr Learned Words Delta Means
```{r}
# rt_data_learnt
# wordrec_data_learnt2
# 
# # wrangle -- need to reduce RTs down to means for each position
# rt_data_learnt_sum_corr <- rt_data_learnt %>% # subject x position
#   summarySE(measurevar = "rt", groupvars = c("subjID","subject","tgt_pos"),na.rm=TRUE) 
# 
# # calculate delta_means for each participant: 
#     # mean_pos3-mean_pos1 / mean_pos1
#   delta_means_learnt <-  data.frame(subj_id=character(), subject=numeric(), delta_mean=numeric(),
#                            stringsAsFactors=FALSE)
#   for (subj in unique(rt_data_learnt_sum_corr$subjID)) {
#     subj_subset <- rt_data_learnt_sum_corr[which(rt_data_learnt_sum_corr$subjID == subj),]  
#     subj_delta <- (subj_subset$rt_mean[3]-subj_subset$rt_mean[1])/subj_subset$rt_mean[1]
#     delta_means_learnt[nrow(delta_means_learnt) + 1,] = list(subj, subj_subset$subject[1], subj_delta)
#   }
#   
# # ensure same subjects
# wordrec_data_learnt2_corr <- wordrec_data_learnt2[wordrec_data_learnt2$subj_id %in% unique(rt_data_learnt_sum_corr$subjID),] # correct! 
#     
# # correlate
# corr_mat_learnt <- cbind(delta_means_learnt, wordrec_data_learnt2_corr$prop_learned)
# colnames(corr_mat_learnt) <- c("subj_id", "subject",  "delta_mean", "prop_learned")
# 
# SL_cortest_learnt <- cor.test(corr_mat_learnt$delta_mean,
#                                corr_mat_learnt$prop_learned, method = "pearson")
# 
# # paired samples
# SL_d_learnt <- cohensD(x = corr_mat_learnt$delta_mean, 
#                         y = corr_mat_learnt$prop_learned, method = "paired")
# 
# # Plot
# ggscatter(corr_mat_learnt, x = "delta_mean", y = "prop_learned", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "pearson",
#           xlab = "% change RT (3rd Pos vs. 1st Pos)", ylab = "Prop. correct word recognition") + 
#   #annotate("text", x = 0.29, y = 0.63, label = paste("N =",toString(N))) +
#   ggtitle('Online & Offline SL Performance for words learned (3 or 4 / 4)') +
#   ggsave(file.path(res_path,'/figures/','/SL_corr_learnedbest.png'), width = w, height = h)
# 
# # Analyze  
# fit <- lm(prop_learned ~ delta_mean, data = corr_mat_learnt)
#   summary(fit)
#   plot(fit)


```

